---
title: "Uncertainty is central for reliable inferences: 
        Using dynamic network features as predictors"
subtitle: "Empirical Example"
author: 
 - name: Björn S. Siepe
   orcid: 0000-0002-9558-4648
   affiliations: University of Marburg
 - name: Matthias Kloft
   orcid: 0000-0003-1845-6957
   affiliations: University of Marburg  
 - name: Fridtjof Petersen
   orcid: 0000-0002-4913-8532
   affiliations: University of Groningen
 - name: Yong Zhang
   orcid: 0000-0002-6313-2575
   affiliations: University of Groningen
 - name: Laura F. Bringmann
   orcid: 0000-0002-8091-9935
   affiliations: University of Groningen
 - name: Daniel W. Heck
   orcid: 0000-0002-6302-9252
   affiliations: University of Marburg
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    fig-width: 7
    fig-height: 4.5
    fig-align: "center"
    embded-resouces: true
execute:
  message: false
  warning: false
  eval: true
params:
  rerun: false  # define parameter if all large analyses should be rerun
---

# Preparation
In this document, we will use an empirical data set to demonstrate the results of different network analysis techniques. 

```{r setup}
# Libraries
library(tidyverse)
library(graphicalVAR)
library(mlVAR)
library(here)
library(gimme)
library(rstan)
library(imputeTS)
library(knitr)
library(gt)
library(bayesplot)

source(here("scripts", "00_functions.R"))
set.seed(35037)
```


# Data 

Load data:
```{r load-data}
data_bringmann <- readRDS(here("data", "data_Bringmann2016.rds"))
```


## Cleaning

Apparently, the neuroticism values are not imported correctly - the 95 values for different IDs are simply shown in the first 95 rows. We need to clean the data first.
```{r clean-data}
data_bringmann <- data_bringmann |> 
  janitor::clean_names()

# obtain unique ids
all_ids <- unique(data_bringmann$subj_id)

# split of the neuroticism column, then reattach it to the correct id
neuroticism_vec <- data_bringmann |> 
  select(subj_id, neuroticism) |> 
  slice(1:95) |> 
  # attach the correct id
  mutate(subj_id = all_ids)

data_bringmann <- data_bringmann |> 
  select(!neuroticism) |> 
  left_join(neuroticism_vec, by = "subj_id")

```


## Descriptives & Missing Values 

We first plot the distributions of all variables: 
```{r descriptives}
data_bringmann |> 
  select(-c(subj_id, neuroticism)) |> 
  gather() |> 
  ggplot(aes(value)) +
  geom_histogram(fill = "#0072B2") +
  facet_wrap(~key, scales = "free") +
  theme_centrality()+
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0))
```
We can see considerable skewness in the "negative" variables. 



Next, we check for missing values by calculating the missingness proportions for each variable and subject:
```{r missing-values}
data_bringmann |> 
  select(-c(neuroticism)) |> 
  group_by(subj_id) |> 
  summarise_all(~sum(is.na(.x))/n()) |>
  select(-subj_id) |> 
  gather() |>
  ggplot(aes(value)) +
  geom_histogram(fill = "#0072B2") +
  facet_wrap(~key, scales = "free") +
  theme_centrality()+
  scale_x_continuous(expand = c(0, 0), labels = scales::label_percent()) +
  scale_y_continuous(expand = c(0, 0))
```

Apparently, the missingness is almost identical for all variables. 

We can now check for zero or very low variances per individual, and then filter them out:
```{r zero-variance}
subj_to_exclude <- data_bringmann |> 
  select(-c(neuroticism)) |> 
  group_by(subj_id) |> 
  summarise(across(everything(),
                   ~var(.x, na.rm = TRUE))) |> 
  filter(if_any(everything(), ~.x < 1)) |> 
  pull(subj_id)

data_bringmann <- data_bringmann |> 
  filter(!subj_id %in% subj_to_exclude)

neuroticism_vec_clean <- data_bringmann |> 
  group_by(subj_id) |> 
  distinct(neuroticism) |>
  pull(neuroticism)

subj_to_exclude |> 
  knitr::kable()
```

As we can see, they all have a very low variance for "depressed"" and, in one case, for "dysphoric" and "anxious" as well.

We then create an overview table that gives the average of person-specific means, standard deviations, and non-missing observations for all variables: 

```{r summary-table}
data_bringmann |> 
  select(-c(neuroticism)) |> 
  group_by(subj_id) |> 
  summarize(across(everything(),
                   list(mean = ~round(mean(.x, na.rm = TRUE), 2),
                          sd = ~round(sd(.x, na.rm = TRUE), 2),
                          obs = ~sum(!is.na(.x))),
                   .names = "{.col}_{.fn}")) |> 
  knitr::kable()
```





## Imputation
Some of the methods require imputation, so we impute per person and per variable, using a Kalman filter approach.
```{r impute}
# Try higher number of iterations
new_param <- list(maxit = 5000)

data_bringmann_imputed <- data_bringmann |> 
  select(-neuroticism) |> 
  group_by(subj_id) |> 
  mutate(across(everything(),
                ~imputeTS::na_kalman(.x, optim.control = new_param),
                .names = "{.col}_imp")) |> 
  ungroup() |> 
  left_join(neuroticism_vec, by = "subj_id")

convergence_warnings<- dplyr::last_dplyr_warnings(n = 15)
```

We observe some potential convergence issues here (see [here](https://github.com/SteffenMoritz/imputeTS/issues/60) for more information). In this case, it makes sense to inspect the imputed values for the affected time series. 

```{r impute-convergence-check, eval = FALSE}
# Obtain IDs with convergence issues
convergence_ids <- sapply(convergence_warnings, function(x){
  x$message[[2]] |> 
    str_extract("(?<=subj_id = )\\d+") |> 
    as.numeric()
})

# Check their time series
columns <- c("angry", "depressed", "dysphoric", "anxious", "relaxed", "happy")

pdf(here("figures", "empirical_example_imputations.pdf"))  # Customize width and height as needed
for (i in 1:length(convergence_ids)) {
  for (col in 1:length(columns)) {
    
    dat1 <- data_bringmann_imputed |> 
      filter(subj_id %in% convergence_ids[[i]])
    
    print(imputeTS::ggplot_na_imputations(
      x_with_na = dat1[[columns[col]]], 
      x_with_imputations = dat1[[paste0(columns[col], "_imp")]]
    ))
  }
}

dev.off()
```
They generally all appear reasonable, and it seems like issues often occured in time series with a relatively low variance/floor effects.



We rename the imputed columns and delete the non-imputed ones:
```{r impute-finalize}
data_bringmann_imputed <- data_bringmann_imputed |> 
  select(subj_id, contains("_imp"), neuroticism) |>
  rename_with(~str_remove(.x, "_imp"), contains("_imp"))

```



# Estimation

We will now estimate the different network and subsequent regression models on the data set to predict neuroticism with the temporal outstrength.

We first split off the time-invariant outcome from the rest of the data:
```{r ema-data}
df_data <- data_bringmann_imputed |> 
  select(-c(neuroticism))
```

We also scale all variables per person for the LASSO approach: 
```{r scale}
df_data <- df_data |> 
  group_by(subj_id) |> 
  mutate(across(everything(), ~scale(.x))) |> 
  ungroup()
```


## `graphicalVAR` 

### Network

To estimate idiographic networks, we first split the data and then estimate a graphical VAR model per person.

```{r fit-gvar}
#| eval: !expr params$rerun
# subset data per person
data_list <- split(df_data, ~ subj_id)

vars <- data_bringmann_imputed |> 
  select(-c(subj_id, neuroticism)) |> 
  colnames()

# fit for each individual
fit_gvar <- lapply(data_list, function(x){
    tryCatch({suppressMessages(graphicalVAR::graphicalVAR(x, 
                               nLambda = 50,
                               vars = vars,
                               verbose = FALSE,
                               gamma = 0, 
                               scale = FALSE))}, error = function(e) NA)
  })

# save results
saveRDS(fit_gvar, here("output", "empirical_example", "fit_gvar.rds"))

```

```{r, include = FALSE}
fit_gvar <- readRDS(here("output", "empirical_example", "fit_gvar.rds"))
```


### Regression

We first need to obtain the outstrength and density values for each individual: 
```{r centrality-gvar}
cent_gvar <- purrr::transpose(lapply(fit_gvar, function(x){
    centrality_gvar(x)
  }))

dens_temp_gvar <- unlist(cent_gvar$dens_temp)
outstrength_gvar_first <- sapply(cent_gvar$outstrength, function(x) unname(x[1]))

# Combine into dataframe with neuroticism
# get neuroticism scores of filtered data frame
data_bringmann |> 
  group_by(subj_id) |> 
  distinct(neuroticism) |>
  pull(neuroticisim)

reg_df_gvar <- data.frame(neuroticism = neuroticism_vec_clean,
                          dens_temp = dens_temp_gvar,
                          outstrength = outstrength_gvar_first)

```

Now we can regress neuroticism on outstrength:
```{r reg-gvar}
reg_gvar_outstrength <- lm(neuroticism ~ outstrength, data = reg_df_gvar)
```

And we can regress it on the temporal density:
```{r reg-gvar-dens}
reg_gvar_dens <- lm(neuroticism ~ dens_temp, data = reg_df_gvar)
``` 

## `mlVAR`

### Network

We fit an mlVAR model to the data: 
```{r fit-mlvar}
#| eval: !expr params$rerun

vars <- data_bringmann_imputed |> 
  select(-c(subj_id, neuroticism)) |> 
  colnames()

fit_mlvar <- tryCatch({suppressWarnings(mlVAR::mlVAR(data_bringmann_imputed,
                            vars = vars,
                            idvar = "subj_id",
                            estimator = "lmer",
                            contemporaneous = "correlated",
                            temporal = "correlated",
                            nCores = 1,
                            scale = FALSE))}, error = function(e) NA)


saveRDS(fit_mlvar, here("output", "empirical_example", "fit_mlvar.rds"))
```

```{r, include = FALSE}
fit_mlvar <- readRDS(here("output", "empirical_example", "fit_mlvar.rds"))
```


### Regression

We obtain the network features: 
```{r centrality-mlvar}
cent_mlvar <- centrality_mlvar(fit_mlvar)

dens_temp_mlvar <- unlist(cent_mlvar$dens_temp)
outstrength_mlvar_first <- sapply(cent_mlvar$outstrength, function(x) unname(x[1]))

# Combine into dataframe with neuroticism
reg_df_mlvar <- data.frame(neuroticism = neuroticism_vec_clean,
                          dens_temp = dens_temp_mlvar,
                          outstrength = outstrength_mlvar_first)
```

Now perform both regressions again: 
```{r reg-mlvar}
reg_mlvar_outstrength <- lm(neuroticism ~ outstrength, data = reg_df_mlvar)
```

```{r reg-mlvar-dens}
reg_mlvar_dens <- lm(neuroticism ~ dens_temp, data = reg_df_mlvar)
```

## `GIMME`

### Network

```{r fit-gimme}
#| eval: !expr params$rerun
data_list <- split(df_data, ~ subj_id)

# remove subject_id from each data set
data_list <- lapply(data_list, function(x){
    x |> 
      select(-c(subj_id))
  }) 


fit_gimme <- gimme::gimme(data_list,
                            ar = TRUE,
                            subgroup = TRUE,
                            plot = FALSE,
                            hybrid = FALSE,
                            groupcutoff = .75,
                            subcutoff = .75,
                            VAR = TRUE)

saveRDS(fit_gimme, here("output", "empirical_example", "fit_gimme.rds"))
```

```{r, include = FALSE}
fit_gimme <- readRDS(here("output", "empirical_example", "fit_gimme.rds"))
```


### Regression

```{r centrality-gimme}
cent_gimme <- centrality_gimme(fit_gimme)

dens_temp_gimme <- cent_gimme$dens_temp
outstrength_gimme_first <- sapply(cent_gimme$outstrength, function(x) unname(x[1]))

# Combine into dataframe with neuroticism
reg_df_gimme <- data.frame(neuroticism = neuroticism_vec_clean,
                          dens_temp = dens_temp_gimme,
                          outstrength = outstrength_gimme_first)
```


```{r reg-gimme-outstrength}
reg_gimme_outstrength <- lm(neuroticism ~ outstrength, data = reg_df_gimme)
```

```{r reg-gimmee-dens}
reg_gimme_dens <- lm(neuroticism ~ dens_temp, data = reg_df_gimme)
```


## `BmlVAR` 

For the Bayesian approach, we perform network estimation and regression in one step. 

### Network & Regression

We first need to compile the model, and then estimate it with similar settings as in the simulation study: 
```{r fit-bmlvar}
#| eval: !expr params$rerun

model_name <- "MLVAR_lkj_only_empirical_example"

stan_model <-   rstan::stan_model(
    file = here::here("scripts", "models", paste0(model_name, ".stan")),
    model_name = model_name
  )

n_var <- 6

# indicators for partial correlations
idx_rho <- upper.tri(matrix(1, n_var, n_var, byrow = F)) |>  
      c() |>  
      which()
  
# repeat the outcome because we have two single-predictor regressions
reg_data <- cbind(
    neuroticism_vec_clean,
    neuroticism_vec_clean
  )
Y <- data_bringmann_imputed |> 
    dplyr::select(-c("subj_id", "neuroticism")) |>  
    as.matrix()

# obtain number of time points per person 
n_tp <- data_bringmann_imputed |> 
  group_by(subj_id) |> 
  count() |> 
  pull(n)

n_id <- length(unique(data_bringmann_imputed$subj_id))
  
# Prepare stan data
# TODO change the regression outcomes!
stan_data <- list(
    K = n_var,
    I = n_id,
    P = 2,   # number of regression outcomes
    N_total = nrow(data_bringmann_imputed),
    n_t = n_tp,
    n_pc = n_var * (n_var - 1) / 2,
    idx_rho = array(idx_rho, dim = length(idx_rho)),
    Y = Y,
    reg_covariate = reg_data,
    sparsity = 2,
    mean_center = 0
  )
  
  
# TODO change sampler settings, currently only used for experiments
fit_bmlvar <- rstan::sampling(
  object = stan_model,
  pars = c("Beta_raw", "Intercepts_raw", "L_Theta", "Rho", "lp__"),
  include = FALSE,
  data = stan_data,
  # seed = 2023,
  chains = 2,
  cores = 1,
  warmup = 200,
  iter = 300,
  init = 0,
  control = list(adapt_delta = 0.90),
  verbose = FALSE
  )

```

Centrality estimates are sampled automatically:
```{r centrality-bmlvar}
# Transpose beta matrices for later summaries
# in the DGP, cols represent lagged vars
# but in BmlVAR, rows represent lagged vars
ests_bmlvar <- extract_all_estimates(fit_bmlvar,
                                       n_id = n_id, 
                                       n_var = n_var, 
                                       transpose_beta = TRUE,
                                       pcor_matrix = TRUE)

```

Obtain the posterior samples of the regressions: 
```{r reg-bmlvar}
tempdens_bmlvar <- ests_bmlvar$tempdens_est
outstrength_bmlvar <- ests_bmlvar$outstrength_est
outstrength_bmlvar_first <- sapply(outstrength_bmlvar, function(x) unname(x[1]))

```


# Contrast results 
In this section, we collect and contrast the results of different methods. 

## Temporal Outstrength

```{r temporal-outstrength}

```


## Network Density




## Combined Table 

We combine the results for different network features and network estimation methods in one table: 

Currently, this is based on mock data:

```{r mock-data-table}
methods <- c("graphicalVAR", "mlVAR", "GIMME", "BmlVAR")
outcomes <- c("Density", "Outstrength")

# Create mock data with point estimates, lower, and upper confidence intervals for each method and outcome
mock_data <- data.frame(
  Method = rep(methods, each = 2),
  Outcome = rep(outcomes, times = 4),
  Point_Estimate = runif(8, 0.2, 0.8),
  Lower_Limit = runif(8, 0.1, 0.5),
  Upper_Limit = runif(8, 0.6, 1.0)
)

# Step 2: Reshape Data
# Spread the data for hierarchical column structure
mock_table <- mock_data |> 
  pivot_wider(names_from = Outcome,
                     values_from = c(Point_Estimate, Lower_Limit, Upper_Limit),
                     names_glue = "{Outcome}_{.value}")


```


```{r prepare-table}
# set color palette 
color_palette <- c("#cf1322", "#036FE3")

min_val <- min(mock_table$Density_Point_Estimate, mock_table$Outstrength_Point_Estimate)
max_val <- max(mock_table$Density_Point_Estimate, mock_table$Outstrength_Point_Estimate)

gt_table <- mock_table |> 
  gt(rowname_col = "Method") |> 
  # hierarchical cols
  cols_label(
    `Density_Point_Estimate` = "Point Est.",
    `Density_Lower_Limit` = "95% Low",
    `Density_Upper_Limit` = "95% High",
    `Outstrength_Point_Estimate` = "Point Est.",
    `Outstrength_Lower_Limit` = "95% Low",
    `Outstrength_Upper_Limit` = "95% High"
  ) |> 
  tab_spanner(
    label = "Density",
    columns = c(Density_Point_Estimate, Density_Lower_Limit, Density_Upper_Limit)
  ) |> 
  tab_spanner(
    label = "Outstrength",
    columns = c(Outstrength_Point_Estimate, Outstrength_Lower_Limit, Outstrength_Upper_Limit)
  ) |> 
  # colorblind palette
  data_color(
    columns = c(Density_Point_Estimate, Outstrength_Point_Estimate),
    domain = c(min_val, max_val),
    palette = color_palette) |> 
  # round
  fmt_number(
    columns = everything(),
    decimals = 2
  ) |> 
  tab_header(
    title = "Comparison of Methods Across Two Outcomes",
  ) |> 
  cols_align(
    align = "center",
    columns = everything()
  )

gt_table

# save to LaTeX
gt_table |> 
  gtsave(here("output", "empirical_example", "mock_table.tex"))

```






# Addition: Bayesian Model Checks

We additionally check the convergence of the Bayesian model by examining convergence statistics and posterior predictive checks.

## Convergence Statistics

We check all Rhats and effective sample sizes:
```{r bmlvar-convergence}

```


## Posterior Predictive

```{r bmlvar-postpred}

```





# Old Code
### Load Data
```{r}
df_affect <-
  read.csv(here("data", "rowland_wenzel_2020", "data_affect.csv")) %>%
  mutate(id = subjno, .before = everything()) %>%
  select(-subjno) %>%
  mutate(group = group - 1)
df_density <-
  read.csv(here("data", "rowland_wenzel_2020", "data_net_density.csv")) 
  # mutate(id = as.factor(subjno) %>% as.numeric(), .before = everything()) %>%
  # select(-subjno)
df <- full_join(df_affect, df_density)

```


### Missing Data Imputation
```{r }
df_imputed <-
  lapply(5:12, function(x)
    imputeTS::na_kalman(df[x])) %>%  
  do.call(cbind, .) %>% 
  cbind(df[1:4], .)
```

```{r}
for(i in 5:12) {
  print(
    imputeTS::ggplot_na_imputations(
      x_with_na = df[, i], 
      x_with_imputations = df_imputed[, i])
  )
}
```

```{r}
Y <- df_imputed[ ,5:12]

I <- length(unique(df_imputed$id))
K <- ncol(Y)
n_pc <-  K * (K - 1) / 2
idx_rho <- upper.tri(matrix(1, K, K, byrow = F)) %>% 
  c() %>% 
  which(.)
n_t <- df_imputed %>% 
  group_by(id) %>% 
  summarise(n = n()) %>% 
  pull(n)

mindfullness <- df %>% 
  distinct(id, smaas) %>% select(smaas) %>% mutate(smaas = scale(smaas))  %>% unlist()
```

## Fit VAR Model in Stan
```{r stan data & compilation, renv.ignore = TRUE}
# prepare stan data
stan_data <-
  list(
    K = K,
    I = I,
    N_total = nrow(Y),
    n_t = n_t,
    n_pc = n_pc,
    idx_rho = idx_rho,
    Y = Y,
    reg_covariate = mindfullness
  )
# Choose model to fit
model_name <- "MLVAR_no_regression"
# Compile model
mlvar_model <-
  rstan::stan_model(
    file = here("scripts", "models", paste0(model_name, ".stan")),
    model_name = model_name
  )
```

```{r sampling, message=FALSE, renv.ignore=TRUE, eval=FALSE}
# number of MCMC chains
n_chains <- 4
# Run sampler
mlvar_fit <- rstan::sampling(
  object = mlvar_model,
  data = stan_data,
  seed = 2023,
  chains = n_chains,
  cores = n_chains,
  warmup = 500,
  iter = 1000,
  init = .1,
  control = list(adapt_delta = 0.9),
  verbose = FALSE
)
saveRDS(mlvar_fit, 
        here("fits", paste0("rowland_wenzel_2020", model_name, "_fit.rds")))
```

## Effective sample size (ESS) & Rhat Plots
```{r ,  renv.ignore=TRUE, eval = FALSE}
# color scheme
color_scheme_set(scheme = "purple")
# Effective sample sizes
plot_neff <-
  mcmc_neff_hist(bayesplot::neff_ratio(mlvar_fit), binwidth = .01) +
  labs(title = "A") +
  guides(color = "none", fill = "none") +
  theme(
    legend.text = element_blank(),
    legend.key = element_blank(),
    title = element_text(size = 16, face = "bold")
  )
# Rhat
# BS: Why does this have missings?
plot_rhat <-
  bayesplot::mcmc_rhat_hist(bayesplot::rhat(mlvar_fit)) +
  labs(title = "B") +
  guides(color = "none", fill = "none") +
  theme(
    legend.text = element_blank(),
    legend.key = element_blank(),
    title = element_text(size = 16, face = "bold")
  ) +
  yaxis_text(on = TRUE)
# Combined plot
plot_diagnostics <- grid.arrange(plot_neff, plot_rhat, ncol = 2)
```

```{r}
param_ests <- summarise_draws(mlvar_fit)
```

# Parameter Recovery
### Betas
```{r renv.ignore=TRUE}
t_oad <- df %>% 
  distinct(id, t_oad) %>% select(t_oad) %>% pull()

draws_beta_dens <- rstan::extract(mlvar_fit, "Beta_density", permuted = FALSE) %>% as_draws_array()

bayesplot::mcmc_recover_scatter(x = draws_beta_dens,
                                true = t_oad)

```

```{r renv.ignore=TRUE}
t_oad <- df %>% 
  distinct(id, t_oad) %>% select(t_oad) %>% pull()

draws_beta_dens <- rstan::extract(mlvar_fit, "Beta_density", permuted = FALSE) %>% as_draws_array()

bayesplot::mcmc_recover_scatter(x = draws_beta_dens,
                                true = t_oad)

```


## Regression
```{r message=FALSE, warning=FALSE, renv.ignore=TRUE}
draws_rho_loc <- 
  rstan::extract(mlvar_fit, "rho_loc", permuted = FALSE) %>%
  as_draws_df()
for (n in 1:n_pc) {
 plot <-  bayesplot::mcmc_intervals(
    draws_rho_loc %>%
      select(ends_with(paste0(",", n, "]"))) %>% 
      as_draws_array()) +
    xlim(0,1) 
  print(plot)
}
```
