---
title: "Uncertainty is central for reliable inferences: 
        Using dynamic network features as predictors"
subtitle: "Empirical Example"
author: 
 - name: Björn S. Siepe
   orcid: 0000-0002-9558-4648
   affiliations: University of Marburg
 - name: Matthias Kloft
   orcid: 0000-0003-1845-6957
   affiliations: University of Marburg  
 - name: Fridtjof Petersen
   orcid: 0000-0002-4913-8532
   affiliations: University of Groningen
 - name: Yong Zhang
   orcid: 0000-0002-6313-2575
   affiliations: University of Groningen
 - name: Laura F. Bringmann
   orcid: 0000-0002-8091-9935
   affiliations: University of Groningen
 - name: Daniel W. Heck
   orcid: 0000-0002-6302-9252
   affiliations: University of Marburg
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    fig-width: 7
    fig-height: 4.5
    fig-align: "center"
    embded-resouces: true
execute:
  message: false
  warning: false
  eval: true
params:
  rerun: false  # define parameter if all large analyses should be rerun
---

# Preparation
In this document, we will use an empirical data set to demonstrate the results of different network analysis techniques. 

```{r setup}
# Libraries
library(tidyverse)
library(graphicalVAR)
library(mlVAR)
library(here)
library(gimme)
library(rstan)
library(imputeTS)
library(knitr)
library(gt)
library(bayesplot)
library(broom)
library(MetBrewer)
library(betaDelta)  # double check
library(ggdist)
library(ggh4x)
library(sysfonts)
library(showtext)
library(beeswarm)
source(here("scripts", "00_functions.R"))
set.seed(35037)
```


# Data 

Load data:
```{r load-data}
data_bringmann <- readRDS(here::here("data", "data_Bringmann2016.RDS"))
```


## Cleaning

Apparently, the neuroticism values are not imported correctly - the 95 values for different IDs are simply shown in the first 95 rows. We need to clean the data first.
```{r clean-data}
data_bringmann <- data_bringmann |> 
  janitor::clean_names()

# obtain unique ids
all_ids <- unique(data_bringmann$subj_id)

# split of the neuroticism column, then reattach it to the correct id
neuroticism_vec <- data_bringmann |> 
  select(subj_id, neuroticism) |> 
  slice(1:95) |> 
  # attach the correct id
  mutate(subj_id = all_ids)

data_bringmann <- data_bringmann |> 
  select(!neuroticism) |> 
  left_join(neuroticism_vec, by = "subj_id")

```


## Descriptives & Missing Values 

We first plot the distributions of all variables: 
```{r descriptives}
data_bringmann |> 
  select(-c(subj_id, neuroticism)) |> 
  gather() |> 
  ggplot(aes(value)) +
  geom_histogram(fill = "#0072B2") +
  facet_wrap(~key, scales = "free") +
  theme_centrality()+
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0))
```
We can see considerable skewness in the "negative" variables. 



Next, we check for missing values by calculating the missingness proportions for each variable and subject:
```{r missing-values}
data_bringmann |> 
  select(-c(neuroticism)) |> 
  group_by(subj_id) |> 
  summarise_all(~sum(is.na(.x))/n()) |>
  select(-subj_id) |> 
  gather() |>
  ggplot(aes(value)) +
  geom_histogram(fill = "#0072B2") +
  facet_wrap(~key, scales = "free") +
  theme_centrality()+
  scale_x_continuous(expand = c(0, 0), labels = scales::label_percent()) +
  scale_y_continuous(expand = c(0, 0))
```

Apparently, the missingness is almost identical for all variables. 

Calculate the average missingness per person: 
```{r missings-person}
data_bringmann |> 
  select(-c(neuroticism)) |> 
  group_by(subj_id) |> 
  summarise(across(everything(),
                   ~sum(is.na(.x))/n())) |> 
  summarise(across(everything(),
                   ~mean(.x, na.rm = TRUE))) |> 
  # take average across all variables
  select(!subj_id) |> 
  pull() |>
  mean()
```



We can now check for zero or very low variances per individual, and then filter them out:
```{r zero-variance}
subj_to_exclude <- data_bringmann |> 
  select(-c(neuroticism)) |> 
  group_by(subj_id) |> 
  summarise(across(everything(),
                   ~var(.x, na.rm = TRUE))) |> 
  filter(if_any(everything(), ~.x < 1)) |> 
  pull(subj_id)

data_bringmann <- data_bringmann |> 
  filter(!subj_id %in% subj_to_exclude)

neuroticism_vec_clean <- data_bringmann |> 
  group_by(subj_id) |> 
  distinct(neuroticism) |>
  pull(neuroticism)

subj_to_exclude |> 
  knitr::kable()
```

As we can see, they all have a very low variance for "depressed"" and, in one case, for "dysphoric" and "anxious" as well.

We then create an overview table that gives the average of person-specific means, standard deviations, and non-missing observations for all variables: 

```{r summary-table}
data_bringmann |> 
  select(-c(neuroticism)) |> 
  group_by(subj_id) |> 
  summarize(across(everything(),
                   list(mean = ~round(mean(.x, na.rm = TRUE), 2),
                          sd = ~round(sd(.x, na.rm = TRUE), 2),
                          obs = ~sum(!is.na(.x))),
                   .names = "{.col}_{.fn}")) |> 
  knitr::kable()
```





## Imputation
Some of the methods require imputation, so we impute per person and per variable, using a Kalman filter approach.
```{r impute}
# Try higher number of iterations
new_param <- list(maxit = 5000)

data_bringmann_imputed <- data_bringmann |> 
  select(-neuroticism) |> 
  group_by(subj_id) |> 
  mutate(across(everything(),
                ~imputeTS::na_kalman(.x, optim.control = new_param),
                .names = "{.col}_imp")) |> 
  ungroup() |> 
  left_join(neuroticism_vec, by = "subj_id")

convergence_warnings<- dplyr::last_dplyr_warnings(n = 15)
```

We observe some potential convergence issues here (see [here](https://github.com/SteffenMoritz/imputeTS/issues/60) for more information). In this case, it makes sense to inspect the imputed values for the affected time series. 

```{r impute-convergence-check, eval = FALSE}
# Obtain IDs with convergence issues
convergence_ids <- sapply(convergence_warnings, function(x){
  x$message[[2]] |> 
    str_extract("(?<=subj_id = )\\d+") |> 
    as.numeric()
})

# Check their time series
columns <- c("angry", "depressed", "dysphoric", "anxious", "relaxed", "happy")

pdf(here("figures", "empirical_example_imputations.pdf"))  # Customize width and height as needed
for (i in 1:length(convergence_ids)) {
  for (col in 1:length(columns)) {
    
    dat1 <- data_bringmann_imputed |> 
      filter(subj_id %in% convergence_ids[[i]])
    
    print(imputeTS::ggplot_na_imputations(
      x_with_na = dat1[[columns[col]]], 
      x_with_imputations = dat1[[paste0(columns[col], "_imp")]]
    ))
  }
}

dev.off()
```
They generally all appear reasonable, and it seems like issues often occurred in time series with a relatively low variance/floor effects.



We rename the imputed columns and delete the non-imputed ones:
```{r impute-finalize}
data_bringmann_imputed <- data_bringmann_imputed |> 
  select(subj_id, contains("_imp"), neuroticism) |>
  rename_with(~str_remove(.x, "_imp"), contains("_imp"))

```



# Estimation

We will now estimate the different network and subsequent regression models on the data set to predict neuroticism with the temporal outstrength.

We first split off the time-invariant outcome from the rest of the data:
```{r ema-data}
df_data <- data_bringmann_imputed |> 
  select(-c(neuroticism))
```

We also scale all variables per person for the LASSO approach: 
```{r scale}
df_data <- df_data |> 
  group_by(subj_id) |> 
  mutate(across(everything(), ~scale(.x))) |> 
  ungroup()
```


## `graphicalVAR` 

### Network

To estimate idiographic networks, we first split the data and then estimate a graphical VAR model per person.

```{r fit-gvar}
#| eval: !expr params$rerun
# subset data per person
data_list <- split(df_data, ~ subj_id)

vars <- data_bringmann_imputed |> 
  select(-c(subj_id, neuroticism)) |> 
  colnames()

pre_gvar <- Sys.time()
# fit for each individual
fit_gvar <- lapply(data_list, function(x){
    tryCatch({suppressMessages(graphicalVAR::graphicalVAR(x, 
                               nLambda = 50,
                               vars = vars,
                               verbose = FALSE,
                               gamma = 0, 
                               scale = FALSE))}, error = function(e) NA)
  })

gvar_fit_time <- Sys.time() - pre_gvar
# save results
saveRDS(fit_gvar, here("output", "empirical_example", "fit_gvar.rds"))

```

```{r, include = FALSE}
fit_gvar <- readRDS(here("output", "empirical_example", "fit_gvar.rds"))
```


### Regression

We first need to obtain the outstrength and density values for each individual: 
```{r centrality-gvar}
cent_gvar <- purrr::transpose(lapply(fit_gvar, function(x){
    centrality_gvar(x)
  }))

dens_temp_gvar <- unlist(cent_gvar$dens_temp)
outstrength_gvar_first <- sapply(cent_gvar$outstrength, function(x) unname(x[1]))

# Combine into dataframe with neuroticism
# get neuroticism scores of filtered data frame
reg_df_gvar <- data.frame(neuroticism = neuroticism_vec_clean,
                          dens_temp = dens_temp_gvar,
                          outstrength = outstrength_gvar_first)

```

Now we can regress neuroticism on outstrength:
```{r reg-gvar}
reg_gvar_outstrength <- lm(neuroticism ~ outstrength, data = reg_df_gvar)
```

And we can regress it on the temporal density:
```{r reg-gvar-dens}
reg_gvar_dens <- lm(neuroticism ~ dens_temp, data = reg_df_gvar)
``` 

## `mlVAR`

### Network

We fit an mlVAR model to the data: 
```{r fit-mlvar}
#| eval: !expr params$rerun

vars <- data_bringmann_imputed |> 
  select(-c(subj_id, neuroticism)) |> 
  colnames()

pre_mlvar <- Sys.time()
fit_mlvar <- tryCatch({suppressWarnings(mlVAR::mlVAR(data_bringmann_imputed,
                            vars = vars,
                            idvar = "subj_id",
                            estimator = "lmer",
                            contemporaneous = "correlated",
                            temporal = "correlated",
                            nCores = 1,
                            scale = FALSE))}, error = function(e) NA)

mlvar_fit_time <- Sys.time() - pre_mlvar
saveRDS(fit_mlvar, here("output", "empirical_example", "fit_mlvar.rds"))
```

```{r, include = FALSE}
fit_mlvar <- readRDS(here("output", "empirical_example", "fit_mlvar.rds"))
```


### Regression

We obtain the network features: 
```{r centrality-mlvar}
cent_mlvar <- centrality_mlvar(fit_mlvar)

dens_temp_mlvar <- unlist(cent_mlvar$dens_temp)
outstrength_mlvar_first <- sapply(cent_mlvar$outstrength, function(x) unname(x[1]))

# Combine into dataframe with neuroticism
reg_df_mlvar <- data.frame(neuroticism = neuroticism_vec_clean,
                          dens_temp = dens_temp_mlvar,
                          outstrength = outstrength_mlvar_first)
```

Now perform both regressions again: 
```{r reg-mlvar}
reg_mlvar_outstrength <- lm(neuroticism ~ outstrength, data = reg_df_mlvar)
```

```{r reg-mlvar-dens}
reg_mlvar_dens <- lm(neuroticism ~ dens_temp, data = reg_df_mlvar)
```

## `GIMME`

### Network

```{r fit-gimme}
#| eval: !expr params$rerun
data_list <- split(df_data, ~ subj_id)

# remove subject_id from each data set
data_list <- lapply(data_list, function(x){
    x |> 
      select(-c(subj_id))
  }) 

pre_gimme <- Sys.time()
fit_gimme <- gimme::gimme(data_list,
                            ar = TRUE,
                            subgroup = TRUE,
                            plot = FALSE,
                            hybrid = FALSE,
                            groupcutoff = .75,
                            subcutoff = .75,
                            VAR = TRUE)

gimme_fit_time <- Sys.time()

saveRDS(fit_gimme, here("output", "empirical_example", "fit_gimme.rds"))
```

```{r, include = FALSE}
fit_gimme <- readRDS(here("output", "empirical_example", "fit_gimme.rds"))
```


### Regression

```{r centrality-gimme}
# obtain partial correlations
fit_gimme$contemp_mat <- lapply(1:length(fit_gimme$path_est_mats), function(i){
      gimme_cor_mat(fit_gimme, id = i, n_vars = 6, pcor = TRUE)
})

cent_gimme <- centrality_gimme(fit_gimme, var_only = TRUE)

dens_temp_gimme <- cent_gimme$dens_temp
outstrength_gimme_first <- sapply(cent_gimme$outstrength, function(x) unname(x[1]))

# Combine into dataframe with neuroticism
reg_df_gimme <- data.frame(neuroticism = neuroticism_vec_clean,
                          dens_temp = unlist(dens_temp_gimme),
                          outstrength = outstrength_gimme_first)
```


```{r reg-gimme-outstrength}
reg_gimme_outstrength <- lm(neuroticism ~ outstrength, data = reg_df_gimme)
```

```{r reg-gimmee-dens}
reg_gimme_dens <- lm(neuroticism ~ dens_temp, data = reg_df_gimme)
```


## `BmlVAR` 

For the Bayesian approach, we perform network estimation and regression in one step. 

### Network & Regression

We first need to compile the model, and then estimate it with similar settings as in the simulation study: 
```{r stan_data}
n_var <- 6

# indicators for partial correlations
idx_rho <- upper.tri(matrix(1, n_var, n_var, byrow = F)) |>  
      c() |>  
      which()
  
# repeat the outcome because we have two single-predictor regressions
reg_data <- cbind(
    neuroticism_vec_clean,
    neuroticism_vec_clean
  )
Y <- data_bringmann_imputed |> 
    dplyr::select(-c("subj_id", "neuroticism")) |>  
    as.matrix()

# obtain number of time points per person 
n_tp <- data_bringmann_imputed |> 
  group_by(subj_id) |> 
  count() |> 
  pull(n)

n_id <- length(unique(data_bringmann_imputed$subj_id))
  
# Prepare stan data
stan_data <- list(
    K = n_var,
    I = n_id,
    P = 2,   # number of regression outcomes
    N_total = nrow(data_bringmann_imputed),
    n_t = n_tp,
    n_pc = n_var * (n_var - 1) / 2,
    idx_rho = array(idx_rho, dim = length(idx_rho)),
    Y = Y,
    reg_covariate = reg_data,
    sparsity = 2,
    mean_center = 0
  )
```

```{r fit-bmlvar}
#| eval: !expr params$rerun

model_name <- "MLVAR_lkj_only_empirical_example"

stan_model <-   rstan::stan_model(
    file = here::here("scripts", "models", paste0(model_name, ".stan")),
    model_name = model_name
  )
  
pre_bmlvar <- Sys.time()  
fit_bmlvar <- rstan::sampling(
  object = stan_model,
  pars = c("Beta_raw", "Intercepts_raw", "L_Theta", "Rho", "lp__"),
  include = FALSE,
  data = stan_data,
  chains = 4,
  cores = 4,
  warmup =500,
  iter = 2500,
  init = 0,
  control = list(adapt_delta = 0.99),
  verbose = FALSE
  )

bmlvar_fit_time <- Sys.time() - pre_bmlvar
bmlvar_fit_time
saveRDS(fit_bmlvar, here("output", "empirical_example", "fit_bmlvar_empirical.rds"))
```

Centrality estimates are sampled automatically:
```{r centrality-bmlvar}
fit_bmlvar <- readRDS(here("output", "empirical_example", "fit_bmlvar_empirical.rds"))

# Transpose beta matrices for later summaries
# in the DGP, cols represent lagged vars
# but in BmlVAR, rows represent lagged vars
n_id <- data_bringmann_imputed |> 
  ungroup() |> 
  distinct(subj_id) |> 
  nrow()


ests_bmlvar <- extract_all_estimates(fit_bmlvar,
                                       n_id = n_id, 
                                       n_var = n_var, 
                                       transpose_beta = TRUE,
                                       pcor_matrix = TRUE)

```

Obtain the posterior samples of the regressions: 
```{r reg-bmlvar}
# centrality outcomes
tempdens_bmlvar <- ests_bmlvar$tempdens_est
outstrength_bmlvar <- ests_bmlvar$outstrength_est
outstrength_bmlvar_first <- sapply(outstrength_bmlvar$median, function(x) unname(x[1]))

# regression outcomes
ests_bmlvar$regression_slope_est

summary_bmlvar <- summary(fit_bmlvar)

bmlvar_reg_standardized <- summary_bmlvar |> 
  as.data.frame() |> 
  rownames_to_column(var = "param") |> 
  filter(grepl("_z", param))
```



## Save all

Save all regression results in one object: 

```{r regression-results}
df_regression <- list(
  gvar = list(reg_dens = reg_gvar_dens,
              reg_outstrength = reg_gvar_outstrength,
              est_dens = reg_df_gvar$dens_temp,
              est_outstrength = reg_df_gvar$outstrength),
  mlvar = list(reg_dens = reg_mlvar_dens,
              reg_outstrength = reg_mlvar_outstrength,
              est_dens = reg_df_mlvar$dens_temp,
              est_outstrength = reg_df_mlvar$outstrength
              ),
  gimme = list(reg_dens = reg_gimme_dens,
              reg_outstrength = reg_gimme_outstrength,
              est_dens = reg_df_gimme$dens_temp,
              est_outstrength = reg_df_gimme$outstrength
              ),
  bmlvar = list(
              reg_dens = bmlvar_reg_standardized[2,2],
              reg_outstrength = bmlvar_reg_standardized[1,2],
              est_dens = tempdens_bmlvar$median,
              est_outstrength = outstrength_bmlvar_first
  )
)

saveRDS(df_regression, here("output/empirical_example/regression_empirical_example.RDS"))
```



# Contrast results 
In this section, we collect and contrast the results of different methods. 
```{r load-results, include = FALSE}
df_regression <- readRDS(here::here("output", "empirical_example", "regression_empirical_example.RDS"))
```

Prepare plotting: 

```{r plotting-helpers}
cond_colors <- set_names(ggokabeito::palette_okabe_ito()[c(5, 1, 3, 4)],
                         c("GVAR", "mlVAR", "GIMME", "BmlVAR"))

cond_colors <- set_names(MetBrewer::met.brewer("Johnson")[c(1,2,4,5)],
                         c("GVAR", "mlVAR", "GIMME", "BmlVAR"))
n_id <- length(neuroticism_vec_clean)

```


## Temporal Outstrength
Create a figure that contrasts all individual estimates of the four different estimation methods: 
```{r temporal-outstrength}
df_outstrength <- data.frame(
  method = rep(c("GVAR", "GIMME","mlVAR",  "BmlVAR"), each = n_id),
  est_outstrength = c(
    df_regression$gvar$est_outstrength,
    df_regression$gimme$est_outstrength,
    df_regression$mlvar$est_outstrength,
    df_regression$bmlvar$est_outstrength
  ),
  id = rep(seq(1:n_id), 4)
)

y_limit <- 0.16
outliers <- df_outstrength |> 
  filter(est_outstrength > y_limit) |> 
  mutate(method = factor(method,
                         levels = c("GVAR",  "GIMME", "mlVAR", "BmlVAR"))) |> 
  group_by(method) |> 
  summarize(outlier_values = paste0(round(est_outstrength, 3), collapse = ", "),
            max_outlier = max(est_outstrength)) |> 
  mutate(outlier_values = if_else(method == "GVAR", 
                                  paste0("Large value (", outlier_values, ")\nremoved"), 
                                  paste0("Large value (", outlier_values, ")\nremoved")))

outstrength_dist <- df_outstrength |> 
  mutate(method = factor(method,
                         levels = c("GVAR",  "GIMME", "mlVAR", "BmlVAR"))) |> 
  mutate(id = as.factor(id)) |> 
  ggplot(aes(x = method, y = est_outstrength, fill = method, col = method)) +
  geom_line(aes(group = id), alpha = 0.25)+
  ggdist::geom_dots(scale = 0.9, stackratio = 0.2,  layout = "swarm", linewidth = .15)+
  ggdist::stat_pointinterval(color = "black", interval_size_range = c(1,2))+
  theme_centrality() +
  labs(
    # title = "Raincloud Plot of Estimation Densities",
    x = "Estimation Method",
    y = "Outstrength",
    fill = "Method"
  ) +
  theme(legend.position = "none") + 
  scale_y_continuous(limits = c(0, y_limit))+ 
  scale_fill_manual(values = cond_colors)+ 
  scale_color_manual(values = rep("#D3D3D3",4))+
  # label outliers
  geom_segment(data = outliers,
               aes(x = as.numeric(method), xend = as.numeric(method),
                   y = c(y_limit * 0.85, y_limit * 0.85), yend = c(y_limit, y_limit)),
               arrow = arrow(length = unit(0.2, "cm")),
               color = "grey30")+
  geom_text(data = outliers,
            aes(x = as.numeric(method) + .05, 
                c(y_limit * 0.925, y_limit * 0.925), label = outlier_values),
            color = "grey30", size = 4, inherit.aes = FALSE, hjust = 0)

outstrength_dist
ggsave(here("figures/empirical_example/outstrength_distribution.pdf"), width = 9 * 0.8, height = 6 * 0.8)
```


## Network Density

```{r network-density}
df_density <- data.frame(
  method = rep(c("GVAR", "mlVAR", "GIMME", "BmlVAR"), each = n_id),
  est_dens = c(
    df_regression$gvar$est_dens,
    df_regression$mlvar$est_dens,
    df_regression$gimme$est_dens,
    df_regression$bmlvar$est_dens
  )
)

df_density |> 
    mutate(method = factor(method,
                         levels = c("GVAR", "mlVAR", "GIMME", "BmlVAR"))) |> 
  ggplot(aes(x = method, y = est_dens, fill = method)) +
  ggdist::stat_halfeye(adjust = 0.5, width = 0.6, .width = 0, justification = -0.2) +
  geom_boxplot(width = 0.15, outlier.shape = NA, alpha = 0.3) +
  geom_jitter(width = 0.1, alpha = 0.5) +
  theme_centrality() +
  labs(
    # title = "Raincloud Plot of Estimation Densities",
    x = "Estimation Method",
    y = "Temporal Density",
    fill = "Method"
  ) +
  theme(legend.position = "none") + 
  scale_fill_manual(values = cond_colors)
```




## Combined Table 

We combine the results for different network features and network estimation methods in one table: 

<!-- Currently, this is based on mock data: -->

<!-- ```{r mock-data-table} -->
<!-- methods <- c("GVAR", "mlVAR", "GIMME", "BmlVAR") -->
<!-- outcomes <- c("Density", "Outstrength") -->

<!-- # create mock data -->
<!-- mock_data <- data.frame( -->
<!--   Method = rep(methods, each = 2), -->
<!--   Outcome = rep(outcomes, times = 4), -->
<!--   Point_Estimate = runif(8, 0.2, 0.8), -->
<!--   Lower_Limit = runif(8, 0.1, 0.5), -->
<!--   Upper_Limit = runif(8, 0.6, 1.0) -->
<!-- ) -->

<!-- # reshape data to wider -->
<!-- mock_table <- mock_data |>  -->
<!--   pivot_wider(names_from = Outcome, -->
<!--                      values_from = c(Point_Estimate, Lower_Limit, Upper_Limit), -->
<!--                      names_glue = "{Outcome}_{.value}") -->


<!-- ``` -->



```{r collect-estimates}
methods <- c("GVAR", "mlVAR", "GIMME", "BmlVAR")
outcomes <- c("Density", "Outstrength")


get_standardized_estimate <- function(model_summary, type = c("estimate", "lower_ci", "upper_ci")) {
  type <- match.arg(type)
  standardized_summary <- lm.beta::lm.beta(model_summary, complete.standardization = TRUE)
  tidy_summary <- broom::tidy(standardized_summary, conf.int = TRUE)
  estimate <- tidy_summary$std_estimate[2]
  conf_ints <- confint(betaDelta::BetaDelta(model_summary))
  lower_ci <- conf_ints[1,1]
  upper_ci <- conf_ints[1,2]
  
  
  switch(type,
         estimate = estimate,
         lower_ci = lower_ci,
         upper_ci = upper_ci)
}


df_estimates <- data.frame(
  Method = rep(methods, each = 2),
  Outcome = rep(outcomes, times = 4),
  Point_Estimate = c(
    get_standardized_estimate(reg_gvar_dens, "estimate"),
    get_standardized_estimate(reg_mlvar_dens, "estimate"),
    get_standardized_estimate(reg_gimme_dens, "estimate"),
    bmlvar_reg_standardized[2,]$summary.mean,
    get_standardized_estimate(reg_gvar_outstrength, "estimate"),
    get_standardized_estimate(reg_mlvar_outstrength, "estimate"),
    get_standardized_estimate(reg_gimme_outstrength, "estimate"),
    bmlvar_reg_standardized[1,]$summary.mean
  ),
  Lower_Limit = c(
    get_standardized_estimate(reg_gvar_dens, "lower_ci"),
    get_standardized_estimate(reg_mlvar_dens, "lower_ci"),
    get_standardized_estimate(reg_gimme_dens, "lower_ci"),
    bmlvar_reg_standardized[2,]$summary.2.5.,
    get_standardized_estimate(reg_gvar_outstrength, "lower_ci"),
    get_standardized_estimate(reg_mlvar_outstrength, "lower_ci"),
    get_standardized_estimate(reg_gimme_outstrength, "lower_ci"),
    bmlvar_reg_standardized[1,]$summary.2.5.
  ),
  Upper_Limit = c(
    get_standardized_estimate(reg_gvar_dens, "upper_ci"),
    get_standardized_estimate(reg_mlvar_dens, "upper_ci"),
    get_standardized_estimate(reg_gimme_dens, "upper_ci"),
    bmlvar_reg_standardized[2,]$summary.97.5.,
    get_standardized_estimate(reg_gvar_outstrength, "upper_ci"),
    get_standardized_estimate(reg_mlvar_outstrength, "upper_ci"),
    get_standardized_estimate(reg_gimme_outstrength, "upper_ci"),
    bmlvar_reg_standardized[1,]$summary.97.5.
  )
)
df_estimates <- df_estimates |> 
  pivot_wider(names_from = Outcome,
                     values_from = c(Point_Estimate, Lower_Limit, Upper_Limit),
                     names_glue = "{Outcome}_{.value}")
```



```{r prepare-table}
# set color palette 
color_palette <- c("#cf1322", "#036FE3")
color_palette <- MetBrewer::met.brewer("Hiroshige")[c(1:5, 8:10)]
min_val <- min(df_estimates$Density_Point_Estimate, df_estimates$Outstrength_Point_Estimate)
max_val <- max(df_estimates$Density_Point_Estimate, df_estimates$Outstrength_Point_Estimate)

gt_table <- df_estimates |> 
  gt(rowname_col = "Method") |> 
  # hierarchical cols
  cols_label(
    `Density_Point_Estimate` = "Point Est.",
    `Density_Lower_Limit` = "95% Low",
    `Density_Upper_Limit` = "95% High",
    `Outstrength_Point_Estimate` = "Point Est.",
    `Outstrength_Lower_Limit` = "95% Low",
    `Outstrength_Upper_Limit` = "95% High"
  ) |> 
  tab_spanner(
    label = "Density",
    columns = c(Density_Point_Estimate, Density_Lower_Limit, Density_Upper_Limit)
  ) |> 
  tab_spanner(
    label = "Outstrength",
    columns = c(Outstrength_Point_Estimate, Outstrength_Lower_Limit, Outstrength_Upper_Limit)
  ) |> 
  # colorblind palette
  data_color(
    columns = c(Density_Point_Estimate, Outstrength_Point_Estimate),
    domain = c(min_val, max_val),
    palette = color_palette) |> 
  # round
  fmt_number(
    columns = everything(),
    decimals = 2
  ) |> 
  tab_header(
    title = "Comparison of Methods Across Two Outcomes",
  ) |> 
  cols_align(
    align = "center",
    columns = everything()
  )

gt_table

# save to LaTeX
gt_table |> 
  gtsave(here("output", "empirical_example", "summary_table.tex"))

```






# BmlVAR Results in more detail



## Convergence Statistics
We additionally check the convergence of the Bayesian model by examining convergence statistics.
We check all Rhats and effective sample sizes:
```{r bmlvar-convergence}
fit_bmlvar <- readRDS(here::here("output", "empirical_example", "fit_bmlvar_empirical.rds"))

summary_bmlvar <- rstan::summary(fit_bmlvar,
                                   pars = c("Beta",
                                            "mu_Beta",
                                            "sigma_Beta",
                                            "mu_Intercepts",
                                            "sigma_Intercepts",
                                            "reg_intercept",
                                            "reg_slope_density",
                                            "sigma_residual",
                                            "Intercepts",
                                            "Sigma",
                                            "Rho_vec",
                                            "Beta_out_strength",
                                            "Beta_in_strength",
                                            "Rho_strength",
                                            "mu_regression",
                                            "reg_slope_density_z",
                                            "reg_intercept_z",
                                            "theta_sd"))$summary

# remove some posterior descriptives
summary_bmlvar <- summary_bmlvar[, !(colnames(summary_bmlvar) %in% c("25%", "75%"))]

# convergence diagnostics
rhat_bmlvar_tmp <- summary_bmlvar |> as.data.frame() |> pull(Rhat)
rhat_bmlvar_tmp <- rhat_bmlvar_tmp[!is.nan(rhat_bmlvar_tmp)]
rhat_bmlvar_mean <- mean(rhat_bmlvar_tmp, na.rm = TRUE)
rhat_bmlvar_11 <- sum(rhat_bmlvar_tmp > 1.1)/length(rhat_bmlvar_tmp)
divtrans_bmlvar <- rstan::get_num_divergent(fit_bmlvar)
```

We observed `r divtrans_bmlvar` divergent transitions. 



## Uncertainty of Centrality

### Proportion of most central node
For each individual, we can simply count number of sampling iterations in which any node was the most central node to obtain an uncertainty statistic. 
```{r extract-outstrength}
# Variable names
var_names <- colnames(data_bringmann_imputed |> select(!c(subj_id, neuroticism)))


outstrength_draws <-
    rstan::extract(object = fit_bmlvar, pars = "Beta_out_strength", permute = FALSE) |>
    posterior::as_draws_matrix() |> 
    as.data.frame()

# convert to long
outstrength_long <- outstrength_draws  |> 
  mutate(iteration = row_number()) |>  
  pivot_longer(
    cols = starts_with("Beta_out_strength"),
    names_to = c("id", "variable"),
    names_pattern = "Beta_out_strength\\[(\\d+),(\\d+)\\]",
    values_to = "outstrength"
  ) |> 
  mutate(id = as.factor(id), 
         variable = as.factor(variable))


```

We now calculate the proportion of having the highest outstrength for each variable: 
```{r prop-highest-centrality}
highest_outstrength <- outstrength_long |>
  group_by(iteration, id) |> 
  filter(outstrength == max(outstrength)) |> 
  ungroup()

variable_counts <- highest_outstrength |>
  group_by(id, variable) |>
  summarise(count = n(), .groups = "drop")

total_iterations <- outstrength_long |>
  group_by(id) |>
  summarise(total = n_distinct(iteration), .groups = "drop") 

all_combinations <- expand.grid(
  id = unique(outstrength_long$id),
  variable = unique(outstrength_long$variable)
)

complete_counts <- all_combinations |>
  left_join(variable_counts, by = c("id", "variable")) |>
  mutate(count = replace_na(count, 0)) # Replace NA counts with 0

proportions <- complete_counts |>
  left_join(total_iterations, by = "id") |>
  mutate(proportion = count / total) |>
  select(id, variable, proportion)


```


Visualize proportions: 
```{r viz-most-central-prop}
proportions |> 
  ggplot(aes(y = variable, 
             x = proportion, 
             group = variable,
             color = variable))+
  ggdist::stat_histinterval()+
  geom_point(size = .5)+
  theme_centrality()+
  theme(legend.position = "none")

```


### Centrality uncertainty visualizations
We find two participants, one for which the most central node has a lower uncertainty, and one for which it is higher: 

```{r two-examples-centrality}
outstrength_bmlvar <- ests_bmlvar$outstrength_est

max_outstrength <- sapply(outstrength_bmlvar$median, which.max)
outstrength_df <- data.frame(
  id = 1:92,
  most_cent = max_outstrength
)

# attach the proportions (in an ugly manner, I know)
extreme_props <- outstrength_df |> 
  mutate(id = as.factor(id),
         most_cent = as.factor(most_cent)) |> 
  left_join(proportions, by = c("id" = "id", "most_cent" = "variable")) |> 
  arrange(proportion) |> 
  mutate(
  lowest = min(proportion),
  highest = max(proportion)
  ) |> 
  filter(proportion == lowest | proportion == highest) |> 
  mutate(most_cent = as.numeric(most_cent)) |> 
  mutate(most_cent = case_match(most_cent, 
    1 ~ var_names[1],
    2 ~ var_names[2],
    3 ~ var_names[3],
    4 ~ var_names[4],
    5 ~ var_names[5],
    6 ~ var_names[6]
  ))

extreme_ids <- as.numeric(unique(extreme_props$id))

proportion_labels <- proportions |> 
  filter(id %in% extreme_ids) |> 
  mutate(id = paste0("Participant ", id)) |> 
  mutate(proportion = sub("^(-?)0.", "\\1.",sprintf("%.2f", proportion))) |> 
  mutate(variable = factor(variable, levels = 1:6, labels = var_names))

# change alpha based on most cent
proportion_labels <- proportion_labels |>
  mutate(id = as.character(id)) |>
  mutate(variable = as.character(variable)) |>
  left_join(extreme_props |>
               select(id, most_cent) |>
              mutate(id = as.character(id),
                     most_cent = as.character(most_cent)) |>
              mutate(id = paste0("Participant ", id)),
            by = "id") |>
  # change alpha based on most cent
  mutate(alpha = if_else(variable == most_cent, 
                         1, 0.5))



# for each participant, add the string "p(c_p = c_max)" to the plot above the first row
# and evaluate the text as formula
proportion_title <- proportion_labels |> 
  group_by(id) |> 
  mutate(proportion_title = "p(c[p] == c[max])") |> 
  distinct(id, proportion_title) |> 
  mutate(x = 0.23, y = 6.5)
 
```

We then create uncertainty plots for their proportions: 
```{r centrality-uncertainty}
# extract and plot their posterior samples
most_central_example_plot <- outstrength_long |> 
  filter(id %in% extreme_ids) |> 
  left_join(proportions, by = c("id" = "id", "variable" = "variable")) |> 
  mutate(id = paste0("Participant ", id)) |> 
  # rename variables with "var_names" based on their order
  mutate(variable = factor(variable, levels = 1:6, labels = var_names)) |>
  ggplot(aes(x = outstrength, y = variable))+
  ggdist::stat_halfeye(.width = c(.66, .95), 
                       fill = cond_colors[4],
                       point_fill = "grey70",
                       point_color = "grey70",
                       color = "grey70",
                       point_alpha = 1,
                       interval_alpha = 1,
                       scale = 1.1)+
  # add proportion_labels as text for each variable
  geom_text(data = proportion_labels,
            aes(x = 0.23, y = variable, label = proportion),
            hjust = 0, vjust = -0.8, size = 4, color = "#6d6d6e")+
  # add title for proportions
  geom_text(data = proportion_title,
            aes(x = x, y = y, label = proportion_title),
            hjust = 0.4, vjust = 0, size = 4, parse = TRUE, color = "#6d6d6e")+
  facet_wrap2(~id,
              axes = "all")+
  theme_centrality()+
  theme(axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size = 14),
        strip.text.x.top = element_text(18))+
  labs(y = "", x = "Outstrength")

ggsave(here("figures", "empirical_example", "most_central_example_plot.pdf"), width = 9 * 0.8, height = 6 * 0.8)

most_central_example_plot
```



## Posterior Predictive

```{r bmlvar-postpred}

```






# Print to normal R script

```{r, eval = FALSE}
knitr::purl(here::here("scripts", "02_empirical_example_bringmann_2016.qmd"), 
            output = here::here("scripts", "02_empirical_example_bringmann_2016.R"),
            documentation = 2)
```




