---
title: "Using features of dynamic networks to guide treatment selection and outcome prediction"
subtitle: "Data-Generating Processes"
author: 
 - name: Björn S. Siepe
   orcid: 0000-0002-9558-4648
   affiliations: University of Marburg
 - name: Matthias Kloft
   orcid: 0000-0003-1845-6957
   affiliations: University of Marburg  
 - name: Fridtjof Petersen
   orcid: 0000-0002-4913-8532
   affiliations: University of Groningen
 - name: Yong Zhang
   orcid: 0000-0002-6313-2575
   affiliations: University of Groningen
 - name: Laura F. Bringmann
   orcid: 0000-0002-8091-9935
   affiliations: University of Groningen
 - name: Daniel W. Heck
   orcid: 0000-0002-6302-9252
   affiliations: University of Marburg
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    fig-width: 7
    fig-height: 4.5
    fig-align: "center"
    embed-resources: true
execute:
  message: false
  warning: false
  eval: true
params:
  rerun: false  # define parameter if all large analyses should be rerun
---

# Preparation

All data-generating processes used in the simulation study are created in this document. 
The final DGPS are saved as RDS files in the `data/` folder.


```{r}
library(tidyverse)
library(here)
source(here::here("scripts", "00_functions.R"))
set.seed(35037)
```


# Synthetic DGP based on previous simulation studies. 
We base our DGP previous sim studies (see the preregistration for more information).
```{r}
var_mat <- create_var_matrix(6, 
                          sparse = TRUE,
                          sparsity_proportion = 0.15,
                          boost_factor = 1.25)
colSums(var_mat)                            
rowSums(var_mat)

arr_to_latex(var_mat)
```




Then we can create the corresponding innovation covariance matrix:
```{r}
cov_mat <- create_cov_matrix(6, 
                             off_diag_val = .15,
                              sparse = TRUE, 
                              sparsity_proportion = 0.15,
                              boost_factor = 1.25)
colSums(cov_mat)
rowSums(cov_mat)
arr_to_latex(cov_mat)
```

Create the corresponding pcor matrix:
```{r}
pcor_mat <- -stats::cov2cor(solve(cov_mat))
```

And the corresponding precision matrix: 
```{r}
kappa_mat <- solve(cov_mat)
```


Save the DGP:
```{r}
#| eval: false
graph_semisparse_synth <- list(beta = var_mat, 
                    sigma = cov_mat, 
                    kappa = kappa_mat,
                    pcor = pcor_mat)

saveRDS(graph_semisparse_synth, here("data/graph_semisparse_synth.RDS"))
```


# Revision 2: Additional DGPs

Three additional DGPs for the second revision address reviewer requests:
(A) 6-node network with >70% sparsity, (B) 10-node network with original (semi-sparse) DGM, and (C) 10-node network with sparse DGM. DGPs A and C are created with `exclude_node1 = FALSE`, allowing the boost factor to ensure node 1 retains sufficient centrality after the additional zeroing.


## Test novel implementation of sparsity

Here, we test the impact of the sparsity proportion implemented in our simulation function. A reviewer asked for a considerably more sparse network then our original setup. 
We investigate whether the sparsity proportion is correctly implemented and whether the boost factor can maintain node 1's centrality even when many edges are zeroed. We also check that the resulting matrices are still valid (e.g., positive definite for the covariance matrix) and that the sparsity level matches our expectations. 

```{r test-sparsity-implementation}

# Conditions to probe: (p, sparsity_proportion, boost_factor, exclude_node1)
conditions <- list(
  original_6n    = list(p = 6,  sp = 0.15, bf = 1.25, excl = TRUE),
  highsparse_6n  = list(p = 6,  sp = 0.70, bf = 1.25,  excl = FALSE),
  original_10n   = list(p = 10, sp = 0.15, bf = 1.25, excl = TRUE),
  highsparse_10n = list(p = 10, sp = 0.70, bf = 1.25,  excl = FALSE)
)
n_rep <- 100  # small but sufficient for a sanity check

overall_sparsity_count <- function(mat) {
  sum(mat == 0) / (nrow(mat)^2)
}

results <- purrr::imap_dfr(conditions, function(cond, name) {
  checks <- vapply(seq_len(n_rep), function(s) {
    set.seed(s)
    m <- create_var_matrix(cond$p,
                           sparse            = TRUE,
                           sparsity_proportion = cond$sp,
                           boost_factor      = cond$bf,
                           exclude_node1     = cond$excl, 
                           max_tries = 1000)
    check_node1_most_central(m, n_node = cond$p, min_diff = 0.05)
  }, logical(1))
  sparsities <- vapply(seq_len(n_rep), function(s) {
    set.seed(s)
    m <- create_var_matrix(cond$p,
                           sparse            = TRUE,
                           sparsity_proportion = cond$sp,
                           boost_factor      = cond$bf,
                           exclude_node1     = cond$excl, 
                           max_tries = 1000)
    overall_sparsity_count(m)
  }, numeric(1))
  data.frame(
    condition   = name,
    p           = cond$p,
    target_sp   = cond$sp,
    node1_prop  = mean(checks),
    mean_sp     = round(mean(sparsities), 3),
    min_sp      = round(min(sparsities),  3),
    max_sp      = round(max(sparsities),  3)
  )
})

knitr::kable(results, digits = 3,
             col.names = c("Condition", "p", "Target sparsity",
                           "Node 1 most central", "Mean sparsity",
                           "Min sparsity", "Max sparsity"))
```


## DGP A: 6-node high-sparsity network

This replicates the original 6-node setup but zeroes many more edges (including those connected to node 1), targeting >70% off-diagonal sparsity. `sparsity_proportion = 0.72` on a 6×6 matrix produces approximately 26 zeros out of 30 off-diagonal entries (~87% sparsity). After zeroing, `boost_factor = 1.5` elevates node 1's row and column so it remains the most central node.

```{r dgp-a-6n-sparse}
set.seed(35037)
var_mat_6n_sparse <- create_var_matrix(6,
                                       sparse = TRUE,
                                       sparsity_proportion = 0.70,
                                       boost_factor = 1.25,
                                       exclude_node1 = FALSE)
colSums(abs(var_mat_6n_sparse))  # node 1 should have highest outstrength
rowSums(abs(var_mat_6n_sparse))  # node 1 should have highest instrength

# Check sparsity: proportion of zero off-diagonal entries
overall_sparsity_count(var_mat_6n_sparse)

arr_to_latex(var_mat_6n_sparse)
```

Innovation covariance matrix for DGP A:
```{r dgp-a-6n-sparse-cov}
cov_mat_6n_sparse <- create_cov_matrix(6,
                                       off_diag_val = .15,
                                       sparse = TRUE,
                                       sparsity_proportion = 0.70,
                                       boost_factor = 1.25,
                                       exclude_node1 = FALSE)
colSums(cov_mat_6n_sparse)
rowSums(cov_mat_6n_sparse)
arr_to_latex(cov_mat_6n_sparse)
```

```{r dgp-a-6n-sparse-save}
#| eval: false
pcor_mat_6n_sparse   <- -stats::cov2cor(solve(cov_mat_6n_sparse))
kappa_mat_6n_sparse  <- solve(cov_mat_6n_sparse)

graph_sparse_6n_highsparse <- list(
  beta  = var_mat_6n_sparse,
  sigma = cov_mat_6n_sparse,
  kappa = kappa_mat_6n_sparse,
  pcor  = pcor_mat_6n_sparse
)

saveRDS(graph_sparse_6n_highsparse, here("data/graph_sparse_6n_highsparse.RDS"))
```


## DGP B: 10-node original (semi-sparse) network

Same construction logic as `graph_semisparse_synth` but with p = 10. `sparsity_proportion = 0.15` with `exclude_node1 = TRUE` preserves the same density level as the original 6-node DGP.

```{r dgp-b-10n}
set.seed(35037)
var_mat_10n <- create_var_matrix(10,
                                 sparse = TRUE,
                                 sparsity_proportion = 0.15,
                                 boost_factor = 1.25,
                                 exclude_node1 = TRUE)
colSums(abs(var_mat_10n))
rowSums(abs(var_mat_10n))
arr_to_latex(var_mat_10n)
```

Innovation covariance matrix for DGP B:
```{r dgp-b-10n-cov}
cov_mat_10n <- create_cov_matrix(10,
                                 off_diag_val = .15,
                                 sparse = TRUE,
                                 sparsity_proportion = 0.15,
                                 boost_factor = 1.25,
                                 exclude_node1 = TRUE)
colSums(cov_mat_10n)
rowSums(cov_mat_10n)
arr_to_latex(cov_mat_10n)
```

```{r dgp-b-10n-save}
#| eval: false
pcor_mat_10n  <- -stats::cov2cor(solve(cov_mat_10n))
kappa_mat_10n <- solve(cov_mat_10n)

graph_semisparse_10n <- list(
  beta  = var_mat_10n,
  sigma = cov_mat_10n,
  kappa = kappa_mat_10n,
  pcor  = pcor_mat_10n
)

saveRDS(graph_semisparse_10n, here("data/graph_semisparse_10n.RDS"))
```


## DGP C: 10-node sparse network

Same construction as DGP B but with `sparsity_proportion = 0.72` and `exclude_node1 = FALSE`. For p = 10, this produces approximately 72 zeros out of 90 off-diagonal entries (~80% sparsity).

```{r dgp-c-10n-sparse}
set.seed(35037)
var_mat_10n_sparse <- create_var_matrix(10,
                                        sparse = TRUE,
                                        sparsity_proportion = 0.70,
                                        boost_factor = 1.25,
                                        exclude_node1 = FALSE)
colSums(abs(var_mat_10n_sparse))
rowSums(abs(var_mat_10n_sparse))
overall_sparsity_count(var_mat_10n_sparse)


arr_to_latex(var_mat_10n_sparse)
```

Innovation covariance matrix for DGP C:
```{r dgp-c-10n-sparse-cov}
cov_mat_10n_sparse <- create_cov_matrix(10,
                                        off_diag_val = .15,
                                        sparse = TRUE,
                                        sparsity_proportion = 0.70,
                                        boost_factor = 1.25,
                                        exclude_node1 = FALSE)
colSums(cov_mat_10n_sparse)
rowSums(cov_mat_10n_sparse)
arr_to_latex(cov_mat_10n_sparse)
```

```{r dgp-c-10n-sparse-save}
#| eval: false
pcor_mat_10n_sparse   <- -stats::cov2cor(solve(cov_mat_10n_sparse))
kappa_mat_10n_sparse  <- solve(cov_mat_10n_sparse)

graph_sparse_10n <- list(
  beta  = var_mat_10n_sparse,
  sigma = cov_mat_10n_sparse,
  kappa = kappa_mat_10n_sparse,
  pcor  = pcor_mat_10n_sparse
)

saveRDS(graph_sparse_10n, here("data/graph_sparse_10n.RDS"))
```


