---
title: "Uncertainty is central to reliable inference"
subtitle: "Simulation Study Visualizations"
author: 
 - name: Björn S. Siepe
   orcid: 0000-0002-9558-4648
   affiliations: University of Marburg
 - name: Matthias Kloft
   orcid: 0000-0003-1845-6957
   affiliations: University of Marburg  
 - name: Fridtjof Petersen
   orcid: 0000-0002-4913-8532
   affiliations: University of Groningen
 - name: Yong Zhang
   orcid: 0000-0002-6313-2575
   affiliations: University of Groningen
 - name: Laura F. Bringmann
   orcid: 0000-0002-8091-9935
   affiliations: University of Groningen
 - name: Daniel W. Heck
   orcid: 0000-0002-6302-9252
   affiliations: University of Marburg
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    fig-width: 7
    fig-height: 4.5
    fig-align: "center"
    embed-resources: true
execute:
  message: false
  warning: false
---

# Background

This document contains code to reproduce the visualizations of the simulation study in the manuscript. It also contains additional results not shown in the main manuscript. 

# Preparation

Load relevant packages:

```{r}
library(tidyverse)
library(here)
library(cowplot)
library(ggh4x)
library(ggokabeito)
library(pander)
source(here::here("scripts", "00_functions.R"))
```

<!-- Create some mock simulation results:  -->
<!-- ```{r mock-res} -->
<!-- sim_results <- readRDS(here("sim_prelium_0312.rds")) -->

<!-- # add some mock results -->
<!-- sim_results[3, ] <- sim_results[1, ] -->
<!-- sim_results[4, ] <- sim_results[2, ] -->

<!-- sim_results[3, "n_tp"] <- 120 -->
<!-- sim_results[4, "n_tp"] <- 60 -->

<!-- ``` -->



Load the simulation results: 
```{r}
sim_results <- readRDS(here("output/", "sim_results.rds"))

# Create a cut version of the simulation results without MCMC diagnostics
sim_res_cut <- sim_results |>
  select(-contains("rhat")) |>
  select(-contains("divtrans"))
```


Attach the seed information from the previous simulation output (before resummarization):
#```{r}
#sim_results <- readRDS(here("output/", "sim_results.rds"))
# ```


## Data Wrangling

Prepare dataframe for visualization by giving proper names, removing unnecessary columns, and pivoting longer:
```{r}
sr_edit <- sim_res_cut |> 
  mutate(
    dgp = factor(n_tp, levels = c(60, 120)),
    n_id = factor(n_id, levels = c(75, 200))
    ) |>
  # remove "reg_" from all column names
  rename_with(~str_remove(., "reg_")) |> 
  # remove everything before a "." in the column names
  rename_with(~str_remove(., ".*\\.")) |> 
  # dplyr::select(-c("REPLICATIONS", "SIM_TIME", "SEED", "COMPLETED", "WARNINGS", "RAM_USED", "heterogeneity")) |>
  dplyr::select(-c("heterogeneity")) |> 
  # pivot longer except conditions cols
  pivot_longer(cols = -c("dgp", "n_tp", "n_id"), 
               names_to = "measure", 
               values_to = "value") |> 
  mutate(measure = str_replace(measure, "power_reg", "powerreg"),
         measure = str_replace(measure, "powertwoside_reg", "powertwosidereg"),
         measure = str_replace(measure, "poweroneside_reg", "poweronesidereg"),
         measure = str_replace(measure, "rmse_reg", "rmsereg"),
         measure = str_replace(measure, "bias_reg", "biasreg"),
         measure = str_replace(measure, "mse_reg", "msereg")) |>
  filter(!measure %in% c("strength_sd", "outstrength_sd", "instrength_sd")) |> 
  separate_wider_delim(measure, 
                       delim = "_",
                       names = c("pm", "outcome", "method", "summary")) |> 
  mutate(method = case_when(
    method == "gvar" ~ "GVAR",
    method == "gimme" ~ "GIMME",
    method == "mlvar" ~ "mlVAR",
    method == "bmlvar" ~ "BmlVAR"
  )) |>
  # treat method as factor and order 
  mutate(method = factor(method, levels = c("GVAR", "GIMME", "mlVAR", "BmlVAR"))) |>
  mutate(outcome = case_when(
    outcome == "beta" ~ "Temporal",
    outcome == "pcor" ~ "Contemporaneous",
    .default = outcome
  )) |>
  group_by(dgp, n_tp, n_id, pm, outcome, method) |>
  pivot_wider(names_from = summary, values_from = value) |> 
  ungroup()



```


Prepare different colors and settings for visualization: 
```{r viz-prep}
# meth_colors <- ggokabeito::palette_okabe_ito()[c(5, 1, 2, 3)]
meth_colors <- set_names(MetBrewer::met.brewer("Johnson")[c(1,3,4,5)],
                         c("GVAR", "mlVAR", "GIMME", "BmlVAR"))
```


# Check Warnings and Non-Convergence
Check if any non-convergence occurred:
```{r sim-errors}

```



# Point Estimates

Plot point estimate recovery (RMSE), helpful to understand the overall performance of the different methods.

```{r viz-point-estimates}
plot_mse <- sr_edit |> 
  mutate(mcse = ifelse(is.na(mcse), 0, mcse)) |>
  mutate(outcome = factor(outcome, levels = c("Temporal", "Contemporaneous"))) |>
  filter(pm == "mse") |> 
  ggplot(aes(x = method, 
             y = mean, 
             colour = method
             )) +
  # add vertical line between methods
  geom_vline(colour = "#F3F4F5", xintercept = seq(1.5, 4, 1))+
  geom_errorbar(aes(ymin = mean - 1*mcse,
                            ymax = mean + 1*mcse),
                        width = .8,
                 position = position_dodge(0.7),
                 show.legend = FALSE)+
  geom_point(position = position_dodge(0.7), 
             size = 1.2) +
  ggh4x::facet_nested(n_id ~ outcome + n_tp,
                      axes = "all",
                      remove_labels = "y") +
  scale_x_discrete(guide = guide_axis(angle = 90))+
  scale_y_continuous(expand = c(0, 0), limits = c(0,0.03)) +
  scale_color_manual(values = meth_colors) +
  theme_centrality() +
  theme(legend.position = "none",
        text = element_text(size = 22))+
  labs(title = "",
       x = "Method",
       colour = "Method",
       y = "MSE of Network Estimation")

plot_mse

```

Plot Bias:

```{r viz-bias}
plot_bias <- sr_edit |> 
  mutate(mcse = ifelse(is.na(mcse), 0, mcse)) |>
  mutate(outcome = factor(outcome, levels = c("Temporal", "Contemporaneous"))) |>
  filter(pm == "bias") |> 
  ggplot(aes(x = method, 
             y = mean, 
             colour = method
             )) +
  # add vertical line between methods
  geom_vline(colour = "#F3F4F5", xintercept = seq(1.5, 4, 1))+
  geom_errorbar(aes(ymin = mean - 1*mcse,
                            ymax = mean + 1*mcse),
                        width = .8,
                 position = position_dodge(0.7),
                 show.legend = FALSE)+
  geom_point(position = position_dodge(0.7), 
             size = 1.2) +
  ggh4x::facet_nested(n_id ~ outcome + n_tp,
                      axes = "all",
                      remove_labels = "y") +
  scale_x_discrete(guide = guide_axis(angle = 90))+
  scale_y_continuous(expand = c(0, 0), limits = c(-0.1,0.1)) +
  scale_color_manual(values = meth_colors) +
  theme_centrality() +
  theme(legend.position = "none",
        text = element_text(size = 22))+
  labs(title = "",
       x = "Method",
       colour = "Method",
       y = "Bias of Network Estimation")

plot_bias
```




# Centrality

## Plot most central identical 

```{r viz-most-central}
plot_mostcentral <- sr_edit |> 
  # if mcse is missing, set to 0
  mutate(mcse = ifelse(is.na(mcse), 0, mcse)) |>
  mutate(outcome = factor(outcome, levels = c("Temporal", "Contemporaneous"))) |>
  filter(pm == "mostcent") |> 
  mutate(n_tp = paste0("t = ", n_tp)) |>
  mutate(n_tp = factor(n_tp, levels = c("t = 60", "t = 120"))) |>
  mutate(n_id = paste0("n = ", n_id)) |>
  mutate(n_id = factor(n_id, levels = c("n = 75", "n = 200"))) |>
  ggplot(aes(x = as.factor(n_tp), 
             y = mean,
             group = method,
             colour = method
             )) +
  # horizontal line at chance level of 1/6
  geom_hline(yintercept = 1/6, 
             linetype = 2, 
             alpha = .7)+
  # add vertical line between methods
  geom_vline(colour = "#F3F4F5", xintercept = seq(1.5, 4, 1))+
  geom_errorbar(aes(ymin = mean - 1*mcse,
                            ymax = mean + 1*mcse),
                        width = .5,
                 position = position_dodge(0.7),
                 show.legend = FALSE)+
  geom_point(position = position_dodge(0.7), 
             size = 1.4) +
  # add mean as text above errorbar
    geom_text(aes(label = sprintf("%.2f", mean)),
              position = position_dodge(0.8),
              vjust = -0.6,
              size = 5,
              show.legend = FALSE) +
  ggh4x::facet_nested(n_id ~ outcome,
                      axes = "all",
                      remove_labels = "y") +
  # scale_x_discrete(guide = guide_axis(angle = 90))+
  scale_y_continuous(expand = c(0, 0), limits = c(0,1.1)) +
  scale_color_manual(values = meth_colors) +
  theme_centrality() +
  theme(legend.position = "bottom",
        text = element_text(size = 24),
        
        )+
  labs(title = "",
       x = "Time Points",
       colour = "",
       y = "Proportion of Correct Central Nodes")

ggsave("plot_mostcentral.pdf", plot_mostcentral, height = 6 * 1.3, width = 9 * 1.3,
       path = here::here("figures/"), device = "pdf")

plot_mostcentral

```


## Plot rank correlation of centrality measures

We were interested in the performance of centrality estimation, which we assessed with regard to rank-order performance. As we expected centrality estimates to be biased downwards in some methods due to sparsity assumptions, we computed the rank-order consistency of individual centrality estimates. To do so, we computed the point estimate of network centrality $\hat{c}$ per individual in a data set, which ignored estimation uncertainty. We then estimated the Spearman rank correlation $\hat{\rho}_{i}$ in repetition $i$ of these estimates with the true network centrality $c$ and calculated its average across repetitions as:
\begin{align*}
    \widehat{\rho} = \frac{\sum_{i=1}^{n_{\text{sim}}} \hat{\rho}_i}{n_{\text{sim}}}
\end{align*}
We calculated the MCSE of this correlation via bootstrapping. 
```{r viz-rank-correlation}
plot_rankcor <- sr_edit |> 
  # if mcse is missing, set to 0
  mutate(mcse = ifelse(is.na(mcse), 0, mcse)) |>
  # uselessly used temp and cont instead of beta and pcor here
  mutate(outcome = case_when(
    outcome == "temp" ~ "Temporal",
    outcome == "cont" ~ "Contemporaneous"
  )) |>
  mutate(outcome = factor(outcome, levels = c("Temporal", "Contemporaneous"))) |>
  filter(pm == "rankcor") |> 
  ggplot(aes(x = method, 
             y = mean, 
             colour = method
             )) +
  # add vertical line between methods
  geom_vline(colour = "#F3F4F5", xintercept = seq(1.5, 4, 1))+
  geom_errorbar(aes(ymin = mean - 1*mcse,
                            ymax = mean + 1*mcse),
                        width = .8,
                 position = position_dodge(0.7),
                 show.legend = FALSE)+
  geom_point(position = position_dodge(0.7), 
             size = 1.2) +
  ggh4x::facet_nested(n_id ~ outcome + n_tp,
                      axes = "all",
                      remove_labels = "y") +
  scale_x_discrete(guide = guide_axis(angle = 90))+
  scale_y_continuous(expand = c(0, 0), limits = c(0,1.1)) +
  scale_color_manual(values = meth_colors) +
  theme_centrality() +
  theme(legend.position = "none",
        text = element_text(size = 22))+
  labs(title = "",
       x = "Method",
       colour = "Method",
       y = "Centrality Rank Correlation")


plot_rankcor

ggsave("plot_rankcor.pdf", plot_rankcor, height = 12, width = 16,
       path = here::here("figures/"), device = "pdf")

``` 


![](figures/plot_rankcor.pdf)



# Regression


## Power of Regression

### In- and Outstrength combined
Prep data
```{r viz-regression-power-prep}
# Split data set into three based on true effect
power_df <- sr_edit |> 
  filter(!str_detect(pm, "poweroneside")) |> 
  mutate(pm = str_replace(pm, "powertwoside", "power")) |> 
  filter(str_detect(pm, "power")) |> 
  mutate(outcome = case_when(
    # outcome == "tempdens" ~ "Temporal\nDensity",
    # outcome == "contdens" ~ "Contemporaneous\nDensity",
    outcome == "outstrength" ~ "Temporal\nOutstrength",
    outcome == "strength" ~ "Contemporaneous\nStrength",
    outcome == "instrength" ~ "Temporal\nInstrength"
  )) |>
  # For now, remove contemporaneous strength
  filter(outcome != "Contemporaneous\nStrength") |>
  mutate(n_id = paste0("n = ", n_id)) |>
  mutate(n_id = factor(n_id, levels = c("n = 75", "n = 200"))) |>
  mutate(n_tp = paste0("t = ", n_tp)) |>
  mutate(n_tp = factor(n_tp, levels = c("t = 60", "t = 120"))) |>
  # split pm into two columns, take last number into new column
  separate_wider_delim(pm, delim = "reg", names = c("pm", "true_effect"))

power_list <- split(power_df, power_df$true_effect)
```

Function to create the plots: 

```{r viz-regression-fn}
# Function to create the plot for a given dataframe
power_plot <- function(df) {
  ggplot(df, aes(x = n_tp, 
                 y = mean, 
                 colour = method,
                 fill = method,
                 group = method)) +
    geom_errorbar(aes(ymin = mean - 1 * mcse,
                      ymax = mean + 1 * mcse),
                  width = 0.5,
                  position = position_dodge(0.7),
                  show.legend = FALSE) +
    # add vertical
    geom_vline(colour = "#F3F4F5", xintercept = seq(1.5, 4, 1))+
    geom_point(position = position_dodge(0.7), 
               size = 1.4) +
    ggh4x::facet_nested(n_id ~ outcome,
                        axes = "all",
                        remove_labels = "y") +
    # scale_x_discrete(guide = guide_axis(angle = 90)) +
    scale_y_continuous(expand = c(0, 0), limits = c(-0.1, 1.1)) +
    scale_color_manual(values = meth_colors) +
    theme_centrality() +
    theme(legend.position = "none",
          strip.text.x.top = ggplot2::element_text(size = rel(0.85)),
          ggh4x.facet.nestline = element_line(colour = "#6d6d6e"),
          axis.text = element_text(size = 18)) +
    labs(title = "",
         x = "",
         colour = "",
         fill = "",
         group = "",
         y = "Detection Rate")
}

```


Create the plots and combine them with patchwork
```{r viz-regression-power-combined}
plot_power_list <- lapply(power_list, power_plot)

# add legend to the third plot
plot_3_legend <- plot_power_list[[3]] + 
  theme(legend.position = "bottom",
        text = element_text(size = 25))

# extract legend
legend <- cowplot::get_plot_component(plot_3_legend, 'guide-box-bottom', return_all = TRUE)

# add legend to cowplot

plot_power_combined <- cowplot::plot_grid(plot_power_list[[1]],
                                          plot_power_list[[2]],
                                          plot_power_list[[3]],
                                          legend,
                                          ncol = 1,
                                          nrow = 4,
                                          rel_heights = c(1, 1, 1, 0.1),
                                          labels = c("True Effect: 0", 
                                                     "True Effect: 0.2",
                                                     "True Effect: 0.4",
                                                     ""),
                                          label_fontfamily = "news",
                                          label_size = 18)




ggsave("plot_power_combined.pdf", plot_power_combined, height = 16* 0.95, width = 16* 0.8,
       path = here::here("figures/"))

plot_power_combined

```


How large was the difference between instrength and outstrength?
```{r instrength-outstrength}
power_df |> 
  pivot_wider(id_cols = c(dgp, n_id, n_tp, pm, true_effect, method), 
              names_from = outcome, 
              values_from = c(mean, mcse)) |> 
  filter(true_effect != 0) |> 
  janitor::clean_names() |> 
  mutate(mean_diff = mean_temporal_instrength - mean_temporal_outstrength) |> 
  summarize(mean_mean_diff = mean(mean_diff))

```


## Power and Bias for Outstrength

```{r outstrength-plot}
power_bias_reg_combined_df <- sr_edit |> 
  mutate(pm = str_replace(pm, "powertwoside", "power")) |> 
  filter(!str_detect(pm, "poweroneside")) |>
  filter(str_detect(pm, "power") | str_detect(pm, "biasreg")) |> 
    mutate(outcome = case_when(
    outcome == "outstrength" ~ "Temporal\nOutstrength",
    outcome == "strength" ~ "Contemporaneous\nStrength",
    outcome == "instrength" ~ "Temporal\nInstrength"
  )) |>
  filter(outcome == "Temporal\nOutstrength") |> 
  mutate(n_id = paste0("n = ", n_id)) |>
  mutate(n_id = factor(n_id, levels = c("n = 75", "n = 200"))) |>
  mutate(n_tp = paste0("t = ", n_tp)) |>
  mutate(n_tp = factor(n_tp, levels = c("t = 60", "t = 120"))) |>
  # split pm into two columns, take last number into new column
  separate_wider_delim(pm, delim = "reg", names = c("pm", "true_effect")) |> 
  mutate(method = factor(method, levels = c("GVAR", "mlVAR", "GIMME", "BmlVAR"))) |> 
  mutate(true_effect = paste0("True Effect: .", true_effect)) |> 
  mutate(pm = case_when(
    str_detect(pm, "power") ~ "Detection Rate",
    str_detect(pm, "bias") ~ "Bias"
  ))

plot_power_bias_outstrength <- power_bias_reg_combined_df |>
  ggplot(aes(x = n_tp, 
             y = mean, 
             colour = method,
             fill = method,
             group = method))+
  geom_errorbar(aes(ymin = mean - 1 * mcse,
                      ymax = mean + 1 * mcse),
                  width = 0.5,
                  position = position_dodge(0.8),
                  show.legend = FALSE) +
    # add vertical
    geom_vline(colour = "#F3F4F5", xintercept = seq(1.5, 4, 1))+
    geom_point(position = position_dodge(0.8), 
               size = 1.4) +
    # add mean as text above errorbar
    geom_text(aes(label = round(mean, 2)),
              position = position_dodge(0.8),
              vjust = -0.6,
              size = 5,
              show.legend = FALSE) +
    ggh4x::facet_nested(true_effect + n_id ~ pm,
                        axes = "all",
                        scales = "free_y",
                        independent = "y") +
    facetted_pos_scales(
      y = list(pm == "Bias" ~ scale_y_continuous(expand = c(0, 0), limits = c(-.45, .2)),
               pm == "Detection Rate" ~ scale_y_continuous(expand = c(0, 0), limits = c(-0.1, 1.1)))
    )+
    labs(
      title = "",
      x = "Timepoints",
      colour = "",
      fill = "",
      group = "",
      y = ""
    ) +
    scale_color_manual(values = meth_colors) +
    theme_centrality() +
    theme(legend.position = "bottom",
          ggh4x.facet.nestline = element_line(colour = "#6d6d6e"),
          axis.text = element_text(size = 18),
          # increase all legend element size
          legend.text = element_text(size = 18),
          legend.title = element_text(size = 18),
          legend.key.size = unit(1.5, "lines"),
          strip.text = ggplot2::element_text(size = 24),
          strip.text.x.top = ggplot2::element_text(size = 24)
          )

ggsave("plot_power_bias_outstrength.pdf", 
       plot_power_bias_outstrength, height = 16* 0.95, width = 16* 0.8,
       path = here::here("figures/"))

```



## RMSE and Bias of Regression

Create some utility functions to create plots for different outcomes: 
```{r bias-rmse-functions}
process_data <- function(data, summary) {
  df_clean <- data |> 
    filter(str_detect(pm, summary)) |> 
    mutate(outcome = case_when(
      outcome == "outstrength" ~ "Temporal\nOutstrength",
      outcome == "strength" ~ "Contemporaneous\nStrength",
      outcome == "instrength" ~ "Temporal\nInstrength"
    )) |>
    filter(outcome != "Contemporaneous\nStrength") |> 
    mutate(
      n_id = factor(paste0("n = ", n_id), levels = c("n = 75", "n = 200")),
      n_tp = factor(paste0("t = ", n_tp), levels = c("t = 60", "t = 120"))
    ) |>
    separate_wider_delim(pm, delim = "reg", names = c("pm", "true_effect"))
  
    split(df_clean, df_clean$true_effect)
}

## Generic plotting function
create_regression_plot <- function(df, 
                                   y_label) {
  ggplot(data = df,
         aes(
           x = n_tp,
           y = mean,
           colour = method,
           fill = method,
           group = method
         )) +
    # add horizontal dashed line at zero for bias
    geom_hline(yintercept = 0, linetype = 2, alpha = .4)+
    geom_errorbar(
      aes(ymin = mean - 1 * mcse, ymax = mean + 1 * mcse),
      width = .5,
      position = position_dodge(0.7),
      show.legend = FALSE
    ) +
    geom_point(position = position_dodge(0.7), size = 1.2) +
    ggh4x::facet_nested(n_id ~ outcome,
                        axes = "all",
                        remove_labels = "y") +
    scale_y_continuous(expand = c(0, 0), limits = c(-.45, .2)) +
    scale_color_manual(values = meth_colors) +
    theme_centrality() +
    theme(
      legend.position = "none",
      strip.text.x.top = ggplot2::element_text(size = rel(0.85)),
      ggh4x.facet.nestline = element_line(colour = "#6d6d6e"),
      axis.text = element_text(size = 18)
    ) +
    labs(
      title = "",
      x = "",
      colour = "",
      group = "",
      fill = "",
      y = y_label
    )
}

## Generate and save combined plots
generate_regression_plots <- function(data, summary, y_label, file_name) {
  processed_list <- process_data(data, summary)
  plot_list <- lapply(processed_list, create_regression_plot, y_label = y_label)
  combined_plot <- cowplot::plot_grid(
    plotlist = plot_list, 
    ncol = 1,
    labels = c("True Effect: 0", "True Effect: 0.2", "True Effect: 0.4")
  )
  ggsave(file_name, combined_plot, height = 16 * 0.95, width = 16 * 0.8, 
         path = here::here("figures/"))
}


## RMSE Plot
generate_regression_plots(sr_edit, "rmsereg", "RMSE", "plot_reg_rmse_combined.pdf")

## Bias Plot
generate_regression_plots(sr_edit, "biasreg", "bias", "plot_reg_bias_combined.pdf")

```






# MCMC Diagnostics
We can now look at the Bayesian models in more detail and check if the Rhats are satisfactory, as well as if there were any divergent transitions.

First, look at Rhats:
```{r viz-rhat}
sim_results |> 
  select(bmlvar_diagnostics.rhat_bmlvar_mean) |> 
  rename("Mean Rhat" = bmlvar_diagnostics.rhat_bmlvar_mean) |> 
  knitr::kable()
```

Second, we tabulate divergent transitions:
```{r check-divtrans}
sim_results |> 
  select(contains("divtrans")) |> 
  rename_with(~ str_remove(., "bmlvar_diagnostics."), everything()) |> 
  knitr::kable(col.names = c("Mean Number of DivTrans",
                            "Sum of DivTrans",
                            "Models with Divtrans"))
```



# Create Overview Table for Supplement
Create one long overview table over all performance measures for the supplement.

```{r overview-table}
sim_results |>
  
``` 


# Session Info

```{r session-info}
pander::pander(sessionInfo())
```



