---
title: "Uncertainty is central for reliable inferences: 
        Using dynamic network features as predictors"
subtitle: "Additional partial simulationst"
author: 
 - name: Björn S. Siepe
   orcid: 0000-0002-9558-4648
   affiliations: University of Marburg
 - name: Matthias Kloft
   orcid: 0000-0003-1845-6957
   affiliations: University of Marburg  
 - name: Fridtjof Petersen
   orcid: 0000-0002-4913-8532
   affiliations: University of Groningen
 - name: Yong Zhang
   orcid: 0000-0002-6313-2575
   affiliations: University of Groningen
 - name: Laura F. Bringmann
   orcid: 0000-0002-8091-9935
   affiliations: University of Groningen
 - name: Daniel W. Heck
   orcid: 0000-0002-6302-9252
   affiliations: University of Marburg
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    fig-width: 7
    fig-height: 4.5
    fig-align: "center"
    embed-resources: true
execute:
  message: false
  warning: false
  eval: true # only show code
---
# Background

In this document, we provide some additional small-scale simulations to understand particular results better. Specifically, we want to understand how much the recovery of the most central node improves when we increase its true centrality.

We first load all relevant packages: 
```{r packages}
library(tidyverse)
library(SimDesign)
library(mlVAR)
library(graphicalVAR)
library(gimme)
library(here)
library(future)
library(corpcor)
source(here::here("scripts", "00_functions.R"))
```





## Data-Generating Processes

Load DGP based on estimated network structures:  
```{r, eval=FALSE}
# non-sparse Graph to simulate from
graph_nonsparse <- readRDS(here::here("data/graph_semisparse_synth.RDS"))

# sparse DGP
graph_sparse <- readRDS(here::here("data/graph_semisparse_synth.RDS"))
```



## Setting parameters

We define the conditions and the fixed parameters for the simulation.

```{r params, eval=FALSE}
dgp <- c("sparse")

# Number of timepoints
n_tp <- c(60, 120)

heterogeneity <- "high"

# Simulation parameters
# Number of individuals 
n_id <- c(75, 200)

# true centrality scaling
# i.e., factor with which the true centrality of most central node is scaled
true_cent_scaling <- c(1, 1.25, 1.5)

# Design Conditions
df_design <- SimDesign::createDesign(
  dgp = dgp,
  n_id = n_id,
  heterogeneity = heterogeneity,
  true_cent_scaling = true_cent_scaling,
  n_tp = n_tp
  )

# Number of variables
n_var <- 6

# for regression
reg_error_sd = 1

# Should GIMME use only nondirected contemporaneous effects?
gimme_var_only = TRUE

# Should GIMME return partial correlations?
gimme_pcor = TRUE

# Should data for non-Bayesian methods be person-mean centered?
mean_center = TRUE

sim_pars <- list(
  n_id = n_id,
  n_var = n_var,
  reg_error_sd = reg_error_sd,
  graph_nonsparse = graph_nonsparse,
  graph_sparse = graph_sparse,
  gimme_var_only = gimme_var_only,
  mean_center = mean_center
)
```


As we only need to compute the true SD once, we can simply load it from disk to save time. These SDs are no longer correct, as we have changed the data-generating matrix. However, we are not interested in the outcome prediction here, so we can ignore this part. 
```{r, eval=FALSE}
true_sd <- readRDS(here::here("data", "true_sd_semisparse.RDS"))
names(true_sd) <- c("sd_results_strength", "sd_results_outstrength", "sd_results_instrength")
df_design$strength_sd <- unlist(true_sd$sd_results_strength)
df_design$outstrength_sd <- unlist(true_sd$sd_results_outstrength)
df_design$instrength_sd <- unlist(true_sd$sd_results_instrength)
```



## Simulating Data


```{r generate, eval=FALSE}
sim_generate <- function(condition, fixed_objects = NULL){
  source(here::here("scripts", "00_functions.R"))

  # obtain fixed params
  SimDesign::Attach(fixed_objects)

  dgp_graph <- ifelse(condition$dgp == "sparse", 
                      "graph_sparse", 
                      "graph_nonsparse")
  beta_sd <- ifelse(condition$heterogeneity == "low",
                    0.05,
                    0.075)
  sigma_sd <- ifelse(condition$heterogeneity == "low",
                    0.005,
                    0.005)
  
  # scale kappa random effects w.r.t diagonal elements
  mean_diag_kappa <- mean(diag(fixed_objects[[dgp_graph]]$kappa)) 
  kappa_sd_low <- 0.005 * mean_diag_kappa
  kappa_sd_high <- 0.005 * mean_diag_kappa
  
  kappa_sd <- ifelse(condition$heterogeneity == "low",
                     kappa_sd_low,
                     kappa_sd_high)
  
  # multiple edges of first node with scaling factor
  fixed_objects[[dgp_graph]]$beta[1,] <- fixed_objects[[dgp_graph]]$beta[1,] * condition$true_cent_scaling
  
  
  ml_sim <- sim_gvar_loop(
                     graph = fixed_objects[[dgp_graph]],
                     beta_sd = beta_sd,
                     kappa_sd = kappa_sd,
                     sigma_sd = sigma_sd, 
                     n_person = condition$n_id,
                     n_time = condition$n_tp,
                     n_node = n_var,
                     max_try = 10000,
                     listify = TRUE,
                     sim_pkg = "mlVAR",
                     sparse_sim = TRUE,
                     most_cent_diff_temp = TRUE,
                     most_cent_diff_temp_min = 0.05,
                     most_cent_diff_cont = TRUE,
                     most_cent_diff_cont_min = 0.05,
                     innov_var_fixed_sigma = TRUE)
  if(any(is.na(ml_sim$beta))){
    stop("Generation of Betas failed")
  }
  
  if(any(is.na(ml_sim$pcor))){
    stop("Generation of PCORs failed")
  } 
  
  
  # Obtain true centralities
  true_cent <- centrality_mlvar_sim(ml_sim,
                                    sim_fn = "sim_gvar_loop")

  # Obtain true centralities
  instrength <- sapply(true_cent$instrength, `[`, 1)
  outstrength <- sapply(true_cent$outstrength, `[`, 1)
  strength <- sapply(true_cent$strength, `[`, 1)
  
  
  # Simulate correlated data with true variance of centralities
  # first column is the density to keep track of the density
  # and for compatibility with an old sim function
  sim_correlated <- function(density, 
                             r_true, 
                             sd_true){
  y_matrix <- matrix(NA, nrow = length(density), ncol = length(r_true) + 1)
  y_matrix[, 1] <- density
  
  for (i in seq_along(r_true)) {
    sd_error <- sd_true * sqrt(1 - r_true[i]^2)
    y_matrix[, i + 1] <- r_true[i] * density + rnorm(length(density), mean = 0, sd = sd_error)
  }
  
  return(y_matrix)
  }
  
  covariate_cont_strength <- sim_correlated(density = strength,
                                            r_true = c(0, 0.2, 0.4),
                                            sd_true = condition$strength_sd)
  covariate_in_strength <- sim_correlated(density = instrength, 
                                          r_true = c(0, 0.2, 0.4), 
                                          sd_true = condition$instrength_sd)
  covariate_out_strength <- sim_correlated(density = outstrength, 
                                           r_true = c(0, 0.2, 0.4), 
                                           sd_true = condition$outstrength_sd)
  

  if(sd(instrength) == 0){
    stop("No variation in instrength")
  }
  if(sd(outstrength) == 0){
    stop("No variation in outstrength")
  }
  if(sd(strength) == 0){
    stop("No variation in strength")
  }

  # Sanity checks
  cor_strength <- cor(covariate_cont_strength[,1], covariate_cont_strength)
  cor_instrength <- cor(covariate_in_strength[,1], covariate_in_strength)
  cor_outstrength <- cor(covariate_out_strength[,1], covariate_out_strength)
  
  
  # Return data and true centralities
  ret_data <- list(
    data = ml_sim$data,
    beta = ml_sim$beta_l,
    kappa = ml_sim$kappa_l,
    pcor = ml_sim$pcor_l,
    covariate_cont_strength = covariate_cont_strength,
    covariate_out_strength = covariate_out_strength,
    covariate_in_strength = covariate_in_strength,
    true_cent = true_cent,
    cor_strength = cor_strength,
    cor_instrength = cor_instrength,
    cor_outstrength = cor_outstrength
  )
  
  return(ret_data)
  
  
}
```





## Analysis

```{r data-analysis, eval=FALSE}
sim_analyse <- function(condition, dat, fixed_objects = NULL){
  
  #--- Preparation
  SimDesign::Attach(fixed_objects)
  
  # Check if mean centering option is true, if so, mean center
  if(isTRUE(fixed_objects$mean_center)){
    dat$data_centered <- lapply(dat$data, function(x){
      x |> 
        dplyr::as_tibble() |> 
        dplyr::mutate(across(everything(), ~ . - mean(.)))
      
    })
  } else {
    dat$data_centered <- lapply(dat$data, function(x){
      x |> 
        dplyr::as_tibble()
      
    })
  }
  
  # Concatenate list of data into dataframe with id column
  df_data_centered <- dplyr::bind_rows(purrr::map(dat$data_centered, dplyr::as_tibble)
                              , .id = "ID") |> 
    dplyr::mutate(ID = as.factor(ID))
  
  df_data <- dplyr::bind_rows(purrr::map(dat$data, dplyr::as_tibble)
                              , .id = "ID") |> 
    dplyr::mutate(ID = as.factor(ID))
  
  n_id <- condition$n_id
  
  
  # #--- frequentist mlVAR

  # Fit model
  fit_mlvar <- tryCatch({mlVAR::mlVAR(df_data_centered,
                            vars = paste0("V", seq(1:n_var)),
                            idvar = "ID",
                            estimator = "lmer",
                            contemporaneous = "orthogonal",
                            temporal = "orthogonal",
                            nCores = 1,
                            scale = FALSE)}, error = function(e) NA)
  if(any(is.na(fit_mlvar))){
    stop("mlVAR did not converge.")
  }
  
  

  # Obtain centralities
  cent_mlvar <- centrality_mlvar(fit_mlvar)
  dens_temp_mlvar <- unlist(cent_mlvar$dens_temp)
  dens_cont_mlvar <- unlist(cent_mlvar$dens_cont)
  outstrength_mlvar <- lapply(cent_mlvar$outstrength, function(x) unname(x))
  strength_mlvar <- lapply(cent_mlvar$strength, function(x) unname(x))
  instrength_mlvar <- lapply(cent_mlvar$instrength, function(x) unname(x))
  outstrength_mlvar_first <- sapply(cent_mlvar$outstrength, function(x) unname(x[1]))
  instrength_mlvar_first <- sapply(cent_mlvar$instrength, function(x) unname(x[1]))
  strength_mlvar_first <- sapply(cent_mlvar$strength, function(x) unname(x[1]))
  
  # Create list of subject-specific estimates
  beta_mlvar <- lapply(1:n_id, function(i){
    t(mlVAR::getNet(fit_mlvar,
                  subject = i,
                  type = "temporal",
                  nonsig = "show"))
  })
  pcor_mlvar <- lapply(1:n_id, function(i){
    mlVAR::getNet(fit_mlvar,
                  subject = i,
                  type = "contemporaneous",
                  nonsig = "show")
  })
  
  # # Calculate fixed effects adjacency matrix
  adj_mat_beta <- t(ifelse(
    mlVAR::getNet(fit_mlvar,
       type = "temporal",
       nonsig = "hide") != 0, 1, 0))
  adj_mat_pcor <- ifelse(
    mlVAR::getNet(fit_mlvar,
       type = "contemporaneous",
       nonsig = "hide") != 0, 1, 0)

  # set effects to zero
  beta_mlvar <- lapply(beta_mlvar, function(i){
    i * adj_mat_beta
  })
  pcor_mlvar <- lapply(pcor_mlvar, function(i){
    i * adj_mat_pcor
  })

  # Fit regression
  reg_mlvar_in_strength <- lapply(2:4, function(i) lm(dat$covariate_in_strength[, i] ~ instrength_mlvar_first))
  reg_mlvar_cont_strength <- lapply(2:4, function(i) lm(dat$covariate_cont_strength[, i] ~ strength_mlvar_first))
  reg_mlvar_out_strength <- lapply(2:4, function(i) lm(dat$covariate_out_strength[, i] ~ outstrength_mlvar_first))
  
  rm(fit_mlvar)
  
  #--- Return Results
  # Also return true centralities for comparison later
  ret_results <- list(
    mlvar = list(
      fit_mlvar = list(
        beta = beta_mlvar,
        pcor = pcor_mlvar),
      dens_temp = dens_temp_mlvar,
      dens_cont = dens_cont_mlvar,
      outstrength = outstrength_mlvar,
      strength = strength_mlvar,
      instrength = instrength_mlvar,
      reg_instrength = reg_mlvar_in_strength,
      reg_strength = reg_mlvar_cont_strength,
      reg_outstrength = reg_mlvar_out_strength
    ),
    true_cent = dat$true_cent,
    covariate_cont_strength = dat$covariate_cont_strength,
    covariate_in_strength = dat$covariate_in_strength,
    covariate_out_strength = dat$covariate_out_strength,
    data = dat$data,
    beta = dat$beta,
    kappa = dat$kappa,
    pcor = dat$pcor,
    true_cor_strength = dat$cor_strength,
    true_cor_instrength = dat$cor_instrength,
    true_cor_outstrength = dat$cor_outstrength
  )
  
  
  return(ret_results)
  
}

```



## Summary


```{r summarize, eval=FALSE}
sim_summarise <- function(condition, results, fixed_objects = NULL){
  
  #--- Preparation
  SimDesign::Attach(fixed_objects)
  ret <- list()
  n_id <- condition$n_id
  
  # Global settings
  use_lm_beta <- FALSE
  
  
  #--- Parameter recovery  
  # IMPORTANT: Keep in mind structure of sim object (rows vs. cols)
  #-- RMSE
  summary_calc <- function(results, method, fit, measure, func) {
  sapply(seq_along(results), function(i){
    if(is.null(results[[i]][[method]][[fit]])){
      return(NA)
    } 
    else{
      unlist(func(results[[i]][[method]][[fit]][[measure]], results[[i]][[measure]]))
    }
  })
}

  
  methods <- c("mlvar")
  measures <- c("beta", "pcor")
  funcs <- list("rmse" = rmse_mean_list, 
                "mse" = mse_mean_list, 
                "bias" = bias_mean_list)
  
  # Loop to get summaries and save them into the ret list
  rmse_list <- list()
  mse_list <- list()
  for (method in methods) {
      for (measure in measures) {
        for (func_name in names(funcs)) {
          result_name <- paste(func_name, measure, method, sep = "_")
          calc_list <- summary_calc(
            results, 
            method, 
            paste0("fit_", method), 
            measure, 
            funcs[[func_name]])
          mean_tmp <- colMeans(apply(as.matrix(calc_list), c(1,2), as.numeric))
          ret[[paste0(result_name, "_mean")]] <- mean(mean_tmp)
          if(func_name == "rmse"){
            # calculate MSE, needed for MCSE of RMSE
            mse_tmp <- summary_calc(
            results, 
            method, 
            paste0("fit_", method), 
            measure, 
            funcs[["mse"]])
            mse_mean_tmp <- mean(colMeans(apply(as.matrix(mse_tmp), c(1,2), as.numeric)))
            ret[[paste0(result_name, "_mcse")]] <- sqrt(stats::var(mean_tmp) / 
                                                          (4 * n_rep * mse_mean_tmp))
          }
          else if(func_name == "mse"){
            ret[[paste0(result_name, "_mcse")]] <- sqrt(stats::var(mean_tmp) / n_rep)
          }
          else if(func_name == "bias"){
            ret[[paste0(result_name, "_mcse")]] <- sqrt(stats::var(mean_tmp) / n_rep)
          }
        }
      }
  }

  
    
  #--- Centrality
  #-- Rank-Order between individuals
  calc_correlation <- function(results, method, measure) {
  sapply(seq_along(results), function(i){
    if(is.null(results[[i]][[method]][[paste0("fit_", method)]])){
      return(NA)
    } 
    else{
      stats::cor(results[[i]][[method]][[paste0("dens_", measure)]], 
                 unlist(results[[i]]$true_cent[[paste0("dens_", measure)]]), 
                 method = "spearman")
    }
  })
  }
  
  # Bootstrap the MCSE for the rank correlation
  bootstrap_rankcor <- function(data, n_boot){
    bootstrap_res <- vector("numeric", n_boot)
    for(i in 1:n_boot){
      ind <- sample(1:n_boot, replace = TRUE)
      bootstrap_res[i] <- mean(data[ind], na.rm = TRUE)
    }
      sd(bootstrap_res, na.rm = TRUE)
  }
  
  measures <- c("temp", "cont")
  for (method in methods) {
    for (measure in measures) {
      result_name <- paste("rankcor", measure, method, sep = "_")
      calc_list <- calc_correlation(
        results = results,
        method = method,
        measure = measure)
      mean_tmp <- mean(calc_list)
      sd_tmp <- bootstrap_rankcor(calc_list, 1000)
      ret[[paste0(result_name, "_mean")]] <- mean_tmp
      ret[[paste0(result_name, "_mcse")]] <- sd_tmp
    }
  }
  
    
  #-- Most central within individuals
  calc_most_cent_ident <- function(results, method, measure) {
    sapply(seq_along(results), function(i){
      if(is.null(results[[i]][[method]][paste0("fit_", method)])){
        return(NA)
      } 
      else{
        mci <- most_cent_ident(results[[i]][[method]][[measure]], 
                              results[[i]]$true_cent[[measure]])
        # check if calculation worked to prevent error
        if(!is.vector(mci) |is.null(mci) | is.null(unlist(mci))){
          return(NA)
        }
        colSums(matrix(unlist(mci), 
                      nrow = n_id, 
                      byrow = FALSE))/n_id
      }
    })
  }
  
  measures <- c("instrength", "outstrength", "strength")
  
  for(method in methods){
    for(measure in measures){
      calc_list <- calc_most_cent_ident(
        results = results, 
        method = method, 
        measure = measure)
        mean_tmp <- mean(calc_list, na.rm = TRUE) 
        mcse_tmp <- sqrt(mean_tmp * (1 - mean_tmp) / n_rep)
      if(measure == "outstrength"){
        ret[[paste0("mostcent_beta_", method, "_mean")]] <- mean_tmp
        ret[[paste0("mostcent_beta_", method, "_mcse")]] <- mcse_tmp
        
      } else if(measure == "strength"){
        ret[[paste0("mostcent_pcor_", method, "_mean")]] <- mean_tmp
        ret[[paste0("mostcent_pcor_", method, "_mcse")]] <- mcse_tmp
      }
    }
  }
  
  

  
  
  #--- Regression
  #-- Power
  regression_power <- function(results, 
                               method, 
                               measure,
                               true_coef = c(0,.2,.4),
                               lm_beta = use_lm_beta) {
  sapply(seq_along(results), function(i){
    if(is.null(results[[i]][[method]][[paste0("reg_", measure)]])){
      return(NA)
    } 
    else{
      reg_pvals <- sapply(results[[i]][[method]][[paste0("reg_", measure)]],
                          function(x){
                            if(isTRUE(lm_beta)){
                              res <- summary(lm.beta::lm.beta(x))$coefficients
                              res[2,5]
                            } else{
                              res <- summary(x)$coefficients
                              res[2,4]
                            }})

      # Calculate Empirical detection rate/power
      ifelse(reg_pvals < .05, 1, 0)
    }
  })
  }


  #-- Summary
  true_coef <- c(0, .2, .4)
  regression_summary <- function(results, 
                              method, 
                              measure,
                              true_coef = c(0,.2,.4),
                              lm_beta = use_lm_beta,
                              summary = "rmse") {
  sapply(seq_along(results), function(i){
    if(is.null(results[[i]][[method]][[paste0("reg_", measure)]])){
      return(NA)
    } 
    else{
      reg_coefs <- sapply(results[[i]][[method]][[paste0("reg_", measure)]],
                          function(x){
                            if(isTRUE(lm_beta)){
                              lm.beta::lm.beta(x)$standardized.coefficients
                            } else{
                              x$coefficients
                            }})[2,]   # 2nd row -> beta coef
      # Calculate RMSE
      if(summary == "rmse"){
        sqrt( (reg_coefs - true_coef )^2 )
      } else if(summary == "mse"){
        (reg_coefs - true_coef)^2
      } else if(summary == "bias"){
        reg_coefs - true_coef
      }
        
      
      }
  })
  }
  

  
  
  # exclude bmlvar because of its different data structure
  methods <- c("mlvar")
  measures <- c("instrength", "outstrength", "strength")
  summaries <- c("rmse", "bias", "mse")
  

  for (method in methods) {
      for (measure in measures) {
        for (summary in summaries) {
          # Calculate summary
          result_name_summary <- paste(summary, "reg", measure, method, sep = "_")
          calc_list <- regression_summary(
            results = results, 
            method = method, 
            measure = measure,
            summary = summary)
          mean_tmp <- rowMeans(calc_list, na.rm = TRUE)
          # bit of a hack to add the names for the different correlation
          # levels
          names(mean_tmp) <- paste0(summary, 
                                   "_reg",
                                   c(0, 2, 4),
                                   "_",
                                   measure,
                                   "_",
                                   method,
                                   "_mean")
          ret[[paste0(result_name_summary, "_mean")]] <- mean_tmp
          if(summary == "rmse"){
            # calculate MSE
            mse_tmp <- regression_summary(
            results, 
            method, 
            measure,
            summary = "mse")
            mse_mean_tmp <- rowMeans(mse_tmp, na.rm = TRUE)
            mcse_tmp <- sqrt (apply(calc_list, 1, var, na.rm = TRUE) / (4*n_rep*mse_mean_tmp))
            names(mcse_tmp) <- paste0(summary, 
                                   "_reg",
                                   c(0, 2, 4),
                                   "_",
                                   measure,
                                   "_",
                                   method,
                                   "_mcse")
            ret[[paste0(result_name_summary, "_mcse")]] <- mcse_tmp
          } else if(summary == "mse"){
            mcse_tmp <- sqrt(
              apply(calc_list, 1, var, na.rm = TRUE) / n_rep)
            names(mcse_tmp) <- paste0(summary, 
                                   "_reg",
                                   c(0, 2, 4),
                                   "_",
                                   measure,
                                   "_",
                                   method,
                                   "_mcse")
            ret[[paste0(result_name_summary, "_mcse")]] <- mcse_tmp
          } else if(summary == "bias"){
            mcse_bias <- sqrt(
              apply(calc_list, 1, var, na.rm = TRUE) / n_rep
            )
            names(mcse_bias) <- paste0(summary, 
                                   "_reg",
                                   c(0, 2, 4),
                                   "_",
                                   measure,
                                   "_",
                                   method,
                                   "_mcse")
            ret[[paste0(result_name_summary, "_mcse")]] <- mcse_bias
          }
          # Calculate Power
          result_name_power <- paste("power", "reg", measure, method, sep = "_")
          calc_list_pwr <- regression_power(
            results = results, 
            method = method, 
            measure = measure)
          pwr_mean <- rowMeans(calc_list_pwr, na.rm = TRUE)
          names(pwr_mean) <- paste0("power", 
                                   "_reg",
                                   c(0, 2, 4),
                                   "_",
                                   measure,
                                   "_",
                                   method,
                                   "_mean")
          ret[[paste0(result_name_power, "_mean")]] <- pwr_mean
          pwr_mcse_tmp <- sqrt(
            pwr_mean * (1 - pwr_mean) / n_rep)
          names(pwr_mcse_tmp) <- paste0("power", 
                                   "_reg",
                                   c(0, 2, 4),
                                   "_",
                                   measure,
                                   "_",
                                   method,
                                   "_mcse")
          ret[[paste0(result_name_power, "_mcse")]] <- pwr_mcse_tmp
        }
      }
  }
  
  ret_vec <- unlist(ret, use.names = TRUE)
  return(ret_vec)
  
}


```


## Executing Simulation

```{r run-sim, eval=FALSE}
n_rep <- 5
future::plan(multisession, workers = n_rep)

sim_results <- SimDesign::runSimulation(
                                    design = df_design[c(3,4),], 
                                    replications = n_rep, 
                                    generate = sim_generate, 
                                    analyse = sim_analyse, 
                                    summarise = sim_summarise,
                                    fixed_objects = sim_pars,
                                    parallel = "future",
                                    # parallel = TRUE,
                                    max_errors = 2,
                                    packages = c("tidyverse", 
                                                 "gimme",
                                                 "mlVAR",
                                                 "graphicalVAR",
                                                 "lm.beta",
                                                 "bayestestR",
                                                 "posterior",
                                                 "rstan",
                                                 "corpcor",
                                                 "Rcpp"),
                                    save_results = TRUE,
                                    # debug = "generate",
                                    filename = "most_central_exploration"
                                    # save_seeds = TRUE
                                    )

plan(sequential)



```