---
title: "Using features of dynamic networks to guide treatment selection and outcome prediction"
subtitle: "Centrality values exploration"
author: 
 - name: Björn S. Siepe
   orcid: 0000-0002-9558-4648
   affiliations: University of Marburg
 - name: Matthias Kloft
   orcid: 0000-0003-1845-6957
   affiliations: University of Marburg  
 - name: Fridtjof Petersen
   orcid: 0000-0002-4913-8532
   affiliations: University of Groningen
 - name: Yong Zhang
   orcid: 0000-0002-6313-2575
   affiliations: University of Groningen
 - name: Laura F. Bringmann
   orcid: 0000-0002-8091-9935
   affiliations: University of Groningen
 - name: Daniel W. Heck
   orcid: 0000-0002-6302-9252
   affiliations: University of Marburg
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    fig-width: 7
    fig-height: 4.5
    fig-align: "center"
    embed-resources: true
execute:
  message: false
  warning: false
  eval: true # only show code
---

# Background

In this script, we explore outstrength centrality values across simulation repetitions in more detail. 

```{r}
#| label: load-pkgs
library(tidyverse)
library(pander)
library(flextable)

source(here::here("scripts", "00_functions.R"))
```



# Homogeneous Conditions

We load all condition specific results: 

```{r}
sim_conditions <- list(
  cond1 = readRDS("~/centrality-uncertainty/output/rev1_fixed_sigma/sim_full_rev1_cond14_fixed_sigma.rds-results_pc04798/results-row-1.rds"),
  cond2 = readRDS("~/centrality-uncertainty/output/rev1_fixed_sigma/sim_full_rev1_cond23_fixed_sigma.rds-results_pc04669/results-row-1.rds"),
  cond3 = readRDS("~/centrality-uncertainty/output/rev1_fixed_sigma/sim_full_rev1_cond23_fixed_sigma.rds-results_pc04669/results-row-2.rds"),
  cond4 = readRDS("~/centrality-uncertainty/output/rev1_fixed_sigma/sim_full_rev1_cond14_fixed_sigma.rds-results_pc04798/results-row-2.rds")
)

```


Extract all centrality values and look at their ranks:

```{r}
# function to analyze centrality differences for a condition
analyze_condition <- function(sim_res, condition_name) {
  true_cent <- lapply(sim_res$results, function(x) x$true_cent$outstrength)
  
  # compute ranks (we have 6 nodes, hence the 7)
  rank_centrality <- lapply(true_cent, function(x) {
    vapply(x, function(y) 7 - rank(y), FUN.VALUE = numeric(6))
  })
  
  all_ranks <- abind::abind(rank_centrality, along = 3)
  rank_counts <- apply(all_ranks, c(1, 2), function(x) {
    table(factor(x, levels = 1:6))
  })
  
  aggregated_counts <- as.data.frame.table(rank_counts) |>
    setNames(c("Rank", "Variable", "Repetition", "Count")) |>
    group_by(Variable, Rank) |>
    summarise(Total_Count = sum(Count), .groups = "drop") |>
    pivot_wider(names_from = Rank, values_from = Total_Count) |>
    mutate(across(where(is.numeric), ~ .x / sum(.x, na.rm = TRUE) * 100),
           condition = condition_name, .before = 1)
  
  # rank summary stats
  rank_summaries <- lapply(seq_along(true_cent), function(rep_idx) {
    centralities <- true_cent[[rep_idx]]
    lapply(centralities, function(person_cent) {
      ranks <- 7 - rank(person_cent)
      data.frame(
        variable = 1:6,
        centrality = person_cent,
        rank = ranks
      )
    }) |>
      do.call(rbind, args = _)
  }) |>
    do.call(rbind, args = _)
  
  rank_stats <- rank_summaries |>
    group_by(variable, rank) |>
    summarise(
      mean = mean(centrality),
      min = min(centrality),
      max = max(centrality),
      sd = sd(centrality)
    ) |>
    ungroup() |> 
    mutate(condition = condition_name, .before = 1)
  
  # Relative differences
  true_cent_df <- map2_dfr(true_cent, seq_along(true_cent), ~{
    .x |>
      map_dfr(~ as_tibble(t(as.matrix(.x)), .name_repair = ~ paste0("V", 1:6))) |>
      mutate(repetition = .y, .before = 1)
  }) |>
    rowid_to_column("individual")
  
  centrality_diff <- true_cent_df |>
    rowwise() |>
    mutate(
      most_central = max(across(starts_with("V"))),
      second_most_central = sort(c_across(starts_with("V")), decreasing = TRUE)[2],
      absolute_difference = most_central - second_most_central,
      relative_difference = absolute_difference / most_central,
      condition = condition_name
    ) |>
    ungroup()
  
  list(
    rank_percentages = aggregated_counts,
    rank_stats = rank_stats,
    centrality_diff = centrality_diff
  )
}

# analyze all conditions
results <- map2(sim_conditions, names(sim_conditions), analyze_condition)

# percentages and ranked results
all_rank_percentages <- map_dfr(results, "rank_percentages")
all_rank_stats <- map_dfr(results, "rank_stats")
all_diffs <- map_dfr(results, "centrality_diff")

saveRDS(results, file = here::here("output", "centrality_comparison_homogeneous.rds"))

```


Investigate summary statistics of centrality for each rank:
```{r}
print("Rank Percentages:")
all_rank_percentages |> 
  flextable::flextable()
```



Look at differences between most central and second most central: 
```{r}
all_diffs |>
  group_by(condition) |>
  summarise(
    mean = mean(relative_difference),
    median = median(relative_difference),
    sd = sd(relative_difference),
    min = min(relative_difference),
    max = max(relative_difference)
  )
```


We can visualize these differences and see that they are similar across all simulation conditions:
```{r}
ggplot(all_diffs, aes(x = relative_difference)) +
  geom_density(fill = "grey70") +
  facet_wrap(~condition, ncol = 2) +
  theme_centrality() +
  labs(
    x = "Relative Difference",
    y = "Density"
  )

```








We off-load these results to make space for the heterogeneous conditions below: 

```{r}
rm(sim_conditions)
```


# Heterogeneous Conditions


```{r}
sim_conditions_het <- list(
  cond1 = readRDS("~/centrality-uncertainty/output/rev1_heterogeneous/sim_full_rev1_cond14_heterogeneous.rds-results_pc04798/results-row-1.rds"),
  cond2 = readRDS("~/centrality-uncertainty/output/rev1_heterogeneous/sim_full_rev1_cond23_heterogeneous.rds-results_pc04669/results-row-1.rds"),
  cond3 = readRDS("~/centrality-uncertainty/output/rev1_heterogeneous/sim_full_rev1_cond23_heterogeneous.rds-results_pc04669/results-row-2.rds"),
  cond4 = readRDS("~/centrality-uncertainty/output/rev1_heterogeneous/sim_full_rev1_cond14_heterogeneous.rds-results_pc04798/results-row-2.rds")
)

```

Analyze all conditions: 

```{r}
# analyze all conditions
results_het <- map2(sim_conditions_het, names(sim_conditions_het), analyze_condition)

# percentages and ranked results
all_rank_percentages_het <- map_dfr(results_het, "rank_percentages")
all_rank_stats_het <- map_dfr(results_het, "rank_stats")
all_diffs_het <- map_dfr(results_het, "centrality_diff")

saveRDS(results_het, file = here::here("output", "centrality_comparison_heterogeneous.rds"))

```


Inspect differences between most central and second most central nodes: 

```{r}
all_diffs_het |>
  group_by(condition) |>
  summarise(
    mean = mean(relative_difference),
    median = median(relative_difference),
    sd = sd(relative_difference),
    min = min(relative_difference),
    max = max(relative_difference)
  ) |> 
  knitr::kable()
```

Summarize them into one average across the homogeneous and heterogeneous condition: 

```{r}

mean_diff_central_node <- all_diffs_het |>
  bind_rows(all_diffs) |> 
  summarise(
    mean_diff = mean(relative_difference)
  ) |> pull(mean_diff)

```

On average, the first node was `r round(mean_diff_central_node, 4)*100`% larger than the second most central node. 



# Session Info

```{r}
pander::pander(sessionInfo())
```




