---
title: "Using features of dynamic networks to guide treatment selection and outcome prediction"
subtitle: "Additional Simulations (Revision 2): Node Count and Sparsity"
author: 
 - name: Björn S. Siepe
   orcid: 0000-0002-9558-4648
   affiliations: University of Marburg
 - name: Matthias Kloft
   orcid: 0000-0003-1845-6957
   affiliations: University of Marburg  
 - name: Fridtjof Petersen
   orcid: 0000-0002-4913-8532
   affiliations: University of Groningen
 - name: Yong Zhang
   orcid: 0000-0002-6313-2575
   affiliations: University of Groningen
 - name: Laura F. Bringmann
   orcid: 0000-0002-8091-9935
   affiliations: University of Groningen
 - name: Daniel W. Heck
   orcid: 0000-0002-6302-9252
   affiliations: University of Marburg
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    fig-width: 7
    fig-height: 4.5
    fig-align: "center"
    embed-resources: true
execute:
  message: false
  warning: false
  eval: false # only show code
---

# Background

In this document, we combine the various files for the additional simulations and analyze them together.


# Preparation

Load relevant packages:

```{r}
library(tidyverse)
library(SimDesign)
library(cowplot)
library(showtext)
library(sysfonts)
library(ggokabeito)
library(janitor)
library(ggh4x)
library(pander)
library(MetBrewer)
library(here)
library(lm.beta)

source(here::here("scripts", "00_functions.R"))
```


We then load the simulation results. Due to the computational complexity of the simulation, these are spread across different files in `output\rev2`: 

- `sim_full_rev2_additional_row1_raw.rds`: Results of the first row with 200 iterations for each method 



We then combine these files into a single large file: 







# Data Wrangling

Prepare dataframe for visualization by giving proper names, removing unnecessary columns, and pivoting longer:

```{r}
sr_edit <- sim_res_cut |> 
  mutate(
    dgp = factor(n_tp, levels = c(60, 120)),
    n_id = factor(n_id, levels = c(75, 200))
    ) |>
  # remove "reg_" from all column names
  rename_with(~str_remove(., "reg_")) |> 
  # remove everything before a "." in the column names
  rename_with(~str_remove(., ".*\\.")) |> 
  dplyr::select(-c("REPLICATIONS", "SIM_TIME", "SEED", "COMPLETED", "WARNINGS")) |>
  dplyr::select(-c("heterogeneity")) |> 
  # pivot longer except conditions cols
  pivot_longer(cols = -c("dgp", "n_tp", "n_id"), 
               names_to = "measure", 
               values_to = "value") |> 
  mutate(measure = str_replace(measure, "power_reg", "powerreg"),
         measure = str_replace(measure, "powertwoside_reg", "powertwosidereg"),
         measure = str_replace(measure, "poweroneside_reg", "poweronesidereg"),
         measure = str_replace(measure, "rmse_reg", "rmsereg"),
         measure = str_replace(measure, "bias_reg", "biasreg"),
         measure = str_replace(measure, "mse_reg", "msereg")) |>
  filter(!measure %in% c("strength_sd", "outstrength_sd", "instrength_sd")) |> 
  separate_wider_delim(measure, 
                       delim = "_",
                       names = c("pm", "outcome", "method", "summary")) |> 
  mutate(method = case_when(
    method == "gvar" ~ "GVAR",
    method == "gimme" ~ "GIMME",
    method == "mlvar" ~ "mlVAR",
    method == "bmlvar" ~ "BmlVAR"
  )) |>
  # treat method as factor and order 
  mutate(method = factor(method, levels = c("GVAR", "GIMME", "mlVAR", "BmlVAR"))) |>
  mutate(outcome = case_when(
    outcome == "beta" ~ "Temporal",
    outcome == "pcor" ~ "Contemporaneous",
    .default = outcome
  )) |>
  group_by(dgp, n_tp, n_id, pm, outcome, method) |>
  pivot_wider(names_from = summary, values_from = value) |> 
  ungroup()



```

Prepare different colors and settings for visualization:

```{r viz-prep}
meth_colors <- set_names(MetBrewer::met.brewer("Johnson")[c(1,2,4,5)],
                         c("GVAR", "mlVAR", "GIMME", "BmlVAR"))
```







# Session Info


```{r session-info}
pander::pander(sessionInfo())
```

