---
title: "Using features of dynamic networks to guide treatment selection and outcome prediction"
subtitle: "Additional Simulations (Revision 2): Node Count and Sparsity"
author: 
 - name: Björn S. Siepe
   orcid: 0000-0002-9558-4648
   affiliations: University of Marburg
 - name: Matthias Kloft
   orcid: 0000-0003-1845-6957
   affiliations: University of Marburg  
 - name: Fridtjof Petersen
   orcid: 0000-0002-4913-8532
   affiliations: University of Groningen
 - name: Yong Zhang
   orcid: 0000-0002-6313-2575
   affiliations: University of Groningen
 - name: Laura F. Bringmann
   orcid: 0000-0002-8091-9935
   affiliations: University of Groningen
 - name: Daniel W. Heck
   orcid: 0000-0002-6302-9252
   affiliations: University of Marburg
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    number-sections: true
    theme: cosmo
    code-fold: true
    code-tools: true
    code-summary: "Show the code"
    fig-width: 7
    fig-height: 4.5
    fig-align: "center"
    embed-resources: true
execute:
  message: false
  warning: false
  eval: false # only show code
---

# Background

This script contains additional simulations for the second revision addressing three reviewer requests:

1. **DGP A** (`sparse_6n_highsparse`): 6-node network with >70% sparsity, matching small-world / empirically sparse topologies.
2. **DGP B** (`semisparse_10n`): 10-node network with the original (semi-sparse) data-generating model.
3. **DGP C** (`sparse_10n`): 10-node network with the sparse data-generating model.

All three conditions use a single combination of n_id = 75, n_tp = 120, and high heterogeneity, to keep computation tractable. Only r_true = 0.2 is investigated. DGPs were defined in `04_dgps.qmd` and saved to `data/`.

The DGP graphs themselves must be generated first by running the relevant chunks in `04_dgps.qmd`.

```{r packages}
library(tidyverse)
library(SimDesign)
library(mlVAR)
library(graphicalVAR)
library(gimme)
library(here)
library(future)
library(corpcor)
source(here::here("scripts", "00_functions.R"))
```




# Data Generation

## Data-Generating Processes

Load the three new DGPs created in `04_dgps.qmd`:
```{r load-dgps}
# DGP A: 6-node, high-sparsity (>70% off-diagonal zeroed)
graph_sparse_6n_highsparse <- readRDS(here::here("data/graph_sparse_6n_highsparse.RDS"))

# DGP B: 10-node, original semi-sparse DGM
graph_semisparse_10n <- readRDS(here::here("data/graph_semisparse_10n.RDS"))

# DGP C: 10-node, sparse DGM
graph_sparse_10n <- readRDS(here::here("data/graph_sparse_10n.RDS"))
```



## Setting parameters

```{r params}
# Three DGPs, one condition each
dgp <- c("sparse_6n_highsparse", "semisparse_10n", "sparse_10n")

# Fixed: single combination of n_id and n_tp
n_id  <- 75
n_tp  <- 120

heterogeneity <- "high"

# Design Conditions: one row per DGP
df_design <- SimDesign::createDesign(
  dgp = dgp,
  n_id = n_id,
  heterogeneity = heterogeneity,
  n_tp = n_tp
)

# Number of variables depends on DGP
n_var_lookup <- list(
  sparse_6n_highsparse = 6L,
  semisparse_10n       = 10L,
  sparse_10n           = 10L
)

# for regression
reg_error_sd <- 1

# Should GIMME use only nondirected contemporaneous effects?
gimme_var_only <- TRUE

# Should GIMME return partial correlations?
gimme_pcor <- TRUE

# Should data for non-Bayesian methods be person-mean centered?
mean_center <- TRUE

sim_pars <- list(
  n_id          = n_id,
  n_var_lookup  = n_var_lookup,
  reg_error_sd  = reg_error_sd,
  graph_sparse_6n_highsparse = graph_sparse_6n_highsparse,
  graph_semisparse_10n       = graph_semisparse_10n,
  graph_sparse_10n           = graph_sparse_10n,
  gimme_var_only = gimme_var_only,
  mean_center    = mean_center
)
```

Pre-compiling the Stan model:
```{r precompile}
model_name <- "MLVAR_lkj_only"
sim_pars$mlvar_model <-
  rstan::stan_model(
    file = here::here("scripts", "models", paste0(model_name, ".stan")),
    model_name = model_name
  )
```


We simulate a large number of partial correlation matrices for each DGP condition and compute the implied standard deviation of the node-1 centrality measure. The n_var dimension is taken from `n_var_lookup` per DGP.

```{r true-strength-sd, eval = FALSE}
n_sim_sd <- 30000
sd_results_strength <- sd_results_outstrength <- sd_results_instrength <-
  vector("list", length = nrow(df_design))

for (i in 1:nrow(df_design)) {
  condition <- df_design[i, ]
  
  dgp_graph <- paste0("graph_", condition$dgp)
  n_var_local <- sim_pars$n_var_lookup[[as.character(condition$dgp)]]
  
  # High heterogeneity fixed
  beta_sd  <- 0.075
  sigma_sd <- 0.075
  mean_diag_kappa <- mean(diag(sim_pars[[dgp_graph]]$kappa))
  kappa_sd <- 0.075 * mean_diag_kappa
  
  ml_sim <- sim_gvar_loop(
    graph    = sim_pars[[dgp_graph]],
    beta_sd  = beta_sd,
    kappa_sd = kappa_sd,
    sigma_sd = sigma_sd,
    n_person = n_sim_sd,
    n_time   = condition$n_tp,
    n_node   = n_var_local,
    max_try  = 1000,
    verbose  = FALSE,
    listify  = TRUE,
    sim_pkg  = "mlVAR",
    sparse_sim = TRUE,
    sparse_sim_sigma = TRUE,
    most_cent_diff_temp     = TRUE,
    most_cent_diff_temp_min = 0.05,
    most_cent_diff_cont     = TRUE,
    most_cent_diff_cont_min = 0.05,
    innov_var_fixed_sigma   = TRUE
  )
  
  true_cent <- centrality_mlvar_sim(ml_sim, sim_fn = "sim_gvar_loop")
  
  strength    <- sapply(true_cent$strength,    `[`, 1)
  outstrength <- sapply(true_cent$outstrength, `[`, 1)
  instrength  <- sapply(true_cent$instrength,  `[`, 1)
  
  sd_results_strength[[i]]    <- sd(strength)
  sd_results_outstrength[[i]] <- sd(outstrength)
  sd_results_instrength[[i]]  <- sd(instrength)
}

sd_results <- list(
  sd_results_strength    = sd_results_strength,
  sd_results_outstrength = sd_results_outstrength,
  sd_results_instrength  = sd_results_instrength
)

saveRDS(sd_results, here::here("data", "true_sd_rev2_additional.RDS"))
```

Load pre-computed true SDs:
```{r load-true-sd}
true_sd <- readRDS(here::here("data", "true_sd_rev2_additional.RDS"))
names(true_sd) <- c("sd_results_strength", "sd_results_outstrength", "sd_results_instrength")
df_design$strength_sd    <- unlist(true_sd$sd_results_strength)
df_design$outstrength_sd <- unlist(true_sd$sd_results_outstrength)
df_design$instrength_sd  <- unlist(true_sd$sd_results_instrength)
```



## Simulating Data


```{r generate}
sim_generate <- function(condition, fixed_objects = NULL) {
  source(here::here("scripts", "00_functions.R"))
  
  SimDesign::Attach(fixed_objects)
  
  # Resolve DGP-specific n_var and graph
  n_var    <- fixed_objects$n_var_lookup[[as.character(condition$dgp)]]
  dgp_graph <- paste0("graph_", condition$dgp)
  
  # High heterogeneity throughout
  beta_sd  <- 0.075
  sigma_sd <- 0.075
  mean_diag_kappa <- mean(diag(fixed_objects[[dgp_graph]]$kappa))
  kappa_sd <- 0.075 * mean_diag_kappa
  
  ml_sim <- sim_gvar_loop(
    graph    = fixed_objects[[dgp_graph]],
    beta_sd  = beta_sd,
    kappa_sd = kappa_sd,
    sigma_sd = sigma_sd,
    n_person = condition$n_id,
    n_time   = condition$n_tp,
    n_node   = n_var,
    max_try  = 10000,
    listify  = TRUE,
    sim_pkg  = "mlVAR",
    sparse_sim = TRUE,
    sparse_sim_sigma = TRUE,
    most_cent_diff_temp = TRUE,
    most_cent_diff_temp_min = 0.05,
    most_cent_diff_cont = TRUE,
    most_cent_diff_cont_min = 0.05,
    innov_var_fixed_sigma = TRUE
  )
  
  if (any(is.na(ml_sim$beta))) stop("Generation of Betas failed")
  if (any(is.na(ml_sim$pcor))) stop("Generation of PCORs failed")
  
  # Obtain true centralities
  true_cent   <- centrality_mlvar_sim(ml_sim, sim_fn = "sim_gvar_loop")
  instrength  <- sapply(true_cent$instrength,  `[`, 1)
  outstrength <- sapply(true_cent$outstrength, `[`, 1)
  strength    <- sapply(true_cent$strength,    `[`, 1)
  
  # Simulate correlated outcome variables for all three effect sizes
  # (reporting focuses on r_true = 0.2)
  sim_correlated <- function(density, r_true, sd_true) {
    y_matrix <- matrix(NA, nrow = length(density), ncol = length(r_true) + 1)
    y_matrix[, 1] <- density
    for (i in seq_along(r_true)) {
      sd_error <- sd_true * sqrt(1 - r_true[i]^2)
      y_matrix[, i + 1] <- r_true[i] * density +
        rnorm(length(density), mean = 0, sd = sd_error)
    }
    return(y_matrix)
  }
  
  covariate_cont_strength <- sim_correlated(
    density = strength,    r_true = 0.2, sd_true = condition$strength_sd)
  covariate_in_strength   <- sim_correlated(
    density = instrength,  r_true = 0.2, sd_true = condition$instrength_sd)
  covariate_out_strength  <- sim_correlated(
    density = outstrength, r_true = 0.2, sd_true = condition$outstrength_sd)
  
  if (sd(instrength)  == 0) stop("No variation in instrength")
  if (sd(outstrength) == 0) stop("No variation in outstrength")
  if (sd(strength)    == 0) stop("No variation in strength")
  
  cor_strength    <- cor(covariate_cont_strength[, 1], covariate_cont_strength)
  cor_instrength  <- cor(covariate_in_strength[, 1],   covariate_in_strength)
  cor_outstrength <- cor(covariate_out_strength[, 1],  covariate_out_strength)
  
  ret_data <- list(
    data                    = ml_sim$data,
    beta                    = ml_sim$beta_l,
    kappa                   = ml_sim$kappa_l,
    pcor                    = ml_sim$pcor_l,
    covariate_cont_strength = covariate_cont_strength,
    covariate_out_strength  = covariate_out_strength,
    covariate_in_strength   = covariate_in_strength,
    true_cent               = true_cent,
    cor_strength            = cor_strength,
    cor_instrength          = cor_instrength,
    cor_outstrength         = cor_outstrength
  )
  
  return(ret_data)
}
```



# Analysis

```{r data-analysis}
sim_analyse <- function(condition, dat, fixed_objects = NULL) {
  
  #--- Preparation
  SimDesign::Attach(fixed_objects)
  
  # Resolve DGP-specific n_var (overrides any n_var from Attach)
  n_var <- fixed_objects$n_var_lookup[[as.character(condition$dgp)]]
  
  # Check if mean centering option is true, if so, mean center
  if (isTRUE(fixed_objects$mean_center)) {
    dat$data_centered <- lapply(dat$data, function(x) {
      x |>
        dplyr::as_tibble() |>
        dplyr::mutate(across(everything(), ~ . - mean(.)))
    })
  }
  
  # Concatenate list of data into dataframe with id column
  df_data_centered <- dplyr::bind_rows(
    purrr::map(dat$data_centered, dplyr::as_tibble), .id = "ID") |>
    dplyr::mutate(ID = as.factor(ID))
  
  df_data <- dplyr::bind_rows(
    purrr::map(dat$data, dplyr::as_tibble), .id = "ID") |>
    dplyr::mutate(ID = as.factor(ID))
  
  n_id <- condition$n_id
  
  #--- graphicalVAR
  # fit_gvar <- lapply(dat$data_centered, function(x) {
  #   tryCatch({
  #     suppressMessages(graphicalVAR::graphicalVAR(
  #       x, nLambda = 50, verbose = FALSE, gamma = 0, scale = FALSE))
  #   }, error = function(e) NA)
  # })
  # 
  # if (any(is.na(fit_gvar))) stop("Not all GVAR models converged.")
  # 
  # cent_gvar <- purrr::transpose(lapply(fit_gvar, function(x) centrality_gvar(x)))
  # 
  # dens_temp_gvar  <- unlist(cent_gvar$dens_temp)
  # dens_cont_gvar  <- unlist(cent_gvar$dens_cont)
  # outstrength_gvar <- lapply(cent_gvar$outstrength, function(x) unname(x))
  # instrength_gvar  <- lapply(cent_gvar$instrength,  function(x) unname(x))
  # strength_gvar    <- lapply(cent_gvar$strength,    function(x) unname(x))
  # instrength_gvar_first  <- sapply(cent_gvar$instrength,  function(x) unname(x[1]))
  # strength_gvar_first    <- sapply(cent_gvar$strength,    function(x) unname(x[1]))
  # outstrength_gvar_first <- sapply(cent_gvar$outstrength, function(x) unname(x[1]))
  # 
  # beta_gvar <- lapply(fit_gvar, function(x) x$beta[, -1])
  # pcor_gvar  <- lapply(fit_gvar, function(x) x$PCC)
  # 
  # reg_gvar_in_strength   <- lapply(2, function(i) lm(dat$covariate_in_strength[, i]   ~ instrength_gvar_first))
  # reg_gvar_cont_strength <- lapply(2, function(i) lm(dat$covariate_cont_strength[, i] ~ strength_gvar_first))
  # reg_gvar_out_strength  <- lapply(2, function(i) lm(dat$covariate_out_strength[, i]  ~ outstrength_gvar_first))
  # 
  # rm(fit_gvar)
  # 
  # #--- GIMME
  # fit_gimme <- tryCatch({
  #   gimme::gimme(dat$data_centered,
  #                ar = TRUE, subgroup = TRUE, plot = FALSE, hybrid = FALSE,
  #                groupcutoff = .75, subcutoff = .75, VAR = gimme_var_only)
  # }, error = function(e) NA)
  # 
  # if (any(is.na(fit_gimme))) stop("GIMME did not converge.")
  # 
  # if (isTRUE(gimme_var_only)) {
  #   fit_gimme$contemp_mat <- lapply(
  #     1:length(fit_gimme$path_est_mats), function(i) {
  #       gimme_cor_mat(fit_gimme, id = i, n_vars = n_var,
  #                     pcor = fixed_objects$gimme_pcor)
  #     })
  # }
  # 
  # cent_gimme <- centrality_gimme(fit_gimme, var_only = gimme_var_only)
  # 
  # dens_temp_gimme  <- unlist(cent_gimme$dens_temp)
  # dens_cont_gimme  <- unlist(cent_gimme$dens_cont)
  # outstrength_gimme <- lapply(cent_gimme$outstrength, function(x) unname(x))
  # instrength_gimme  <- lapply(cent_gimme$instrength,  function(x) unname(x))
  # strength_gimme    <- lapply(cent_gimme$strength,    function(x) unname(x))
  # outstrength_gimme_first <- sapply(cent_gimme$outstrength, function(x) unname(x[1]))
  # instrength_gimme_first  <- sapply(cent_gimme$instrength,  function(x) unname(x[1]))
  # strength_gimme_first    <- sapply(cent_gimme$strength,    function(x) unname(x[1]))
  # 
  # beta_gimme <- lapply(fit_gimme$path_est_mats, function(x) x[, 1:n_var])
  # 
  # if (isFALSE(gimme_var_only)) {
  #   pcor_gimme <- lapply(fit_gimme$path_est_mats, function(x) x[, (n_var+1):(n_var*2)])
  # }
  # if (isTRUE(gimme_var_only)) {
  #   pcor_gimme <- lapply(fit_gimme$contemp_mat, function(x) x)
  # }
  # 
  # reg_gimme_in_strength   <- lapply(2, function(i) lm(dat$covariate_in_strength[, i]   ~ instrength_gimme_first))
  # reg_gimme_cont_strength <- lapply(2, function(i) lm(dat$covariate_cont_strength[, i] ~ strength_gimme_first))
  # reg_gimme_out_strength  <- lapply(2, function(i) lm(dat$covariate_out_strength[, i]  ~ outstrength_gimme_first))
  # 
  # rm(fit_gimme)
  # 
  # #--- frequentist mlVAR
  # fit_mlvar <- tryCatch({
  #   suppressWarnings(mlVAR::mlVAR(df_data_centered,
  #                                 vars = paste0("V", seq(1:n_var)),
  #                                 idvar = "ID",
  #                                 estimator = "lmer",
  #                                 contemporaneous = "correlated",
  #                                 temporal = "correlated",
  #                                 nCores = 1,
  #                                 scale = FALSE))
  # }, error = function(e) NA)
  # 
  # if (any(is.na(fit_mlvar))) stop("mlVAR did not converge.")
  # 
  # cent_mlvar <- centrality_mlvar(fit_mlvar)
  # dens_temp_mlvar  <- unlist(cent_mlvar$dens_temp)
  # dens_cont_mlvar  <- unlist(cent_mlvar$dens_cont)
  # outstrength_mlvar <- lapply(cent_mlvar$outstrength, function(x) unname(x))
  # strength_mlvar    <- lapply(cent_mlvar$strength,    function(x) unname(x))
  # instrength_mlvar  <- lapply(cent_mlvar$instrength,  function(x) unname(x))
  # outstrength_mlvar_first <- sapply(cent_mlvar$outstrength, function(x) unname(x[1]))
  # instrength_mlvar_first  <- sapply(cent_mlvar$instrength,  function(x) unname(x[1]))
  # strength_mlvar_first    <- sapply(cent_mlvar$strength,    function(x) unname(x[1]))
  # 
  # beta_mlvar <- lapply(1:n_id, function(i) {
  #   t(mlVAR::getNet(fit_mlvar, subject = i, type = "temporal", nonsig = "show"))
  # })
  # pcor_mlvar <- lapply(1:n_id, function(i) {
  #   mlVAR::getNet(fit_mlvar, subject = i, type = "contemporaneous", nonsig = "show")
  # })
  # 
  # adj_mat_beta <- t(ifelse(
  #   mlVAR::getNet(fit_mlvar, type = "temporal",       nonsig = "hide") != 0, 1, 0))
  # adj_mat_pcor <- ifelse(
  #   mlVAR::getNet(fit_mlvar, type = "contemporaneous", nonsig = "hide") != 0, 1, 0)
  # 
  # beta_mlvar <- lapply(beta_mlvar, function(i) i * adj_mat_beta)
  # pcor_mlvar <- lapply(pcor_mlvar, function(i) i * adj_mat_pcor)
  # 
  # reg_mlvar_in_strength   <- lapply(2, function(i) lm(dat$covariate_in_strength[, i]   ~ instrength_mlvar_first))
  # reg_mlvar_cont_strength <- lapply(2, function(i) lm(dat$covariate_cont_strength[, i] ~ strength_mlvar_first))
  # reg_mlvar_out_strength  <- lapply(2, function(i) lm(dat$covariate_out_strength[, i]  ~ outstrength_mlvar_first))
  # 
  # rm(fit_mlvar)
  
  #--- Bayesian mlVAR
  idx_rho <- upper.tri(matrix(1, n_var, n_var, byrow = FALSE)) |> c() |> which()
  
  reg_data <- cbind(
    dat$covariate_in_strength[, 2],
    dat$covariate_out_strength[, 2],
    dat$covariate_cont_strength[, 2]
  )
  Y <- df_data |> dplyr::select(-"ID") |> as.matrix()
  
  n_tp <- condition$n_tp
  
  stan_data <- list(
    K        = n_var,
    I        = n_id,
    P        = 3,
    N_total  = n_id * n_tp,
    n_t      = rep(n_tp, n_id),
    n_pc     = n_var * (n_var - 1) / 2,
    idx_rho  = array(idx_rho, dim = length(idx_rho)),
    Y        = Y,
    reg_covariate = reg_data,
    reg_cent_type = array(c(1L, 2L, 3L), dim = 3),  # instrength, outstrength, strength
    sparsity = 2,
    mean_center = 1
  )
  
  fit_bmlvar <- rstan::sampling(
    object  = fixed_objects$mlvar_model,
    pars    = c("Beta_raw", "Intercepts_raw", "L_Theta", "Rho", "lp__"),
    include = FALSE,
    data    = stan_data,
    chains  = 4,
    cores   = 1,
    warmup  = 500,
    iter    = 1000,
    init    = 0,
    control = list(adapt_delta = 0.90),
    verbose = FALSE
  )
  
  if (!inherits(fit_bmlvar, "stanfit")) stop("BmlVAR model failed.")
  
  ests_bmlvar <- extract_all_estimates(fit_bmlvar,
                                       n_id = n_id,
                                       n_var = n_var,
                                       transpose_beta = FALSE,
                                       pcor_matrix = TRUE)
  
  dens_temp_bmlvar  <- ests_bmlvar$tempdens_est$median
  dens_cont_bmlvar  <- ests_bmlvar$contdens_est$median
  instrength_bmlvar  <- ests_bmlvar$instrength_est$median
  outstrength_bmlvar <- ests_bmlvar$outstrength_est$median
  strength_bmlvar    <- ests_bmlvar$pcor_centrality_est$median
  outstrength_bmlvar_first <- sapply(ests_bmlvar$outstrength_est$median,        function(x) unname(x[1]))
  strength_bmlvar_first    <- sapply(ests_bmlvar$pcor_centrality_est$median,    function(x) unname(x[1]))
  instrength_bmlvar_first  <- sapply(ests_bmlvar$instrength_est$median,         function(x) unname(x[1]))
  
  reg_bmlvar <- list(
    regression_intercept = ests_bmlvar$regression_intercept_est,
    regression_slope     = ests_bmlvar$regression_slope_est
  )
  
  summary_bmlvar <- rstan::summary(fit_bmlvar,
    pars = c("Beta", "mu_Beta", "sigma_Beta",
             "mu_Intercepts", "sigma_Intercepts",
             "reg_intercept", "reg_slope_density", "sigma_residual",
             "Intercepts", "Sigma", "Rho_vec",
             "Beta_out_strength", "Beta_in_strength", "Rho_strength",
             "mu_regression", "reg_slope_density_z",
             "reg_intercept_z", "theta_sd"))$summary
  
  summary_bmlvar <- summary_bmlvar[, !(colnames(summary_bmlvar) %in% c("25%", "75%"))]
  
  rhat_bmlvar_tmp  <- summary_bmlvar |> as.data.frame() |> pull(Rhat)
  rhat_bmlvar_tmp  <- rhat_bmlvar_tmp[!is.nan(rhat_bmlvar_tmp)]
  rhat_bmlvar_mean <- mean(rhat_bmlvar_tmp, na.rm = TRUE)
  rhat_bmlvar_11   <- sum(rhat_bmlvar_tmp > 1.1) / length(rhat_bmlvar_tmp)
  divtrans_bmlvar  <- rstan::get_num_divergent(fit_bmlvar)
  
  rm(fit_bmlvar)
  
  #--- Return Results
  ret_results <- list(
    gvar = list(
NULL
    ),
    gimme = list(
NULL
    ),
    mlvar = list(
NULL
    ),
    bmlvar = list(
      fit_bmlvar = list(
        beta = ests_bmlvar$beta_est$median,
        pcor = ests_bmlvar$pcor_est$median
      ),
      dens_temp   = dens_temp_bmlvar,
      dens_cont   = dens_cont_bmlvar,
      outstrength = outstrength_bmlvar,
      strength    = strength_bmlvar,
      instrength  = instrength_bmlvar,
      reg_bmlvar  = reg_bmlvar,
      ests_bmlvar = ests_bmlvar,
      summary_bmlvar   = summary_bmlvar,
      rhat_bmlvar_mean = rhat_bmlvar_mean,
      rhat_bmlvar_11   = rhat_bmlvar_11,
      divtrans_bmlvar  = divtrans_bmlvar
    ),
    true_cent               = dat$true_cent,
    covariate_cont_strength = dat$covariate_cont_strength,
    covariate_in_strength   = dat$covariate_in_strength,
    covariate_out_strength  = dat$covariate_out_strength,
    data  = dat$data,
    beta  = dat$beta,
    kappa = dat$kappa,
    pcor  = dat$pcor,
    true_cor_strength    = dat$cor_strength,
    true_cor_instrength  = dat$cor_instrength,
    true_cor_outstrength = dat$cor_outstrength
  )
  
  # Output the list locally
  filename <- sprintf('additional_simulations_only_bayes_fit_%i.rds', condition$REPLICATION)
  saveRDS(object = ret_results, 
          file = paste0(here::here("output", "rev2"), filename))
  
  return(ret_results)
}
```



# Summary

```{r summarize}
sim_summarise <- function(condition, results, fixed_objects = NULL) {
  
  #--- Preparation
  SimDesign::Attach(fixed_objects)
  ret  <- list()
  n_id <- condition$n_id
  
  use_lm_beta <- FALSE
  
  #--- Parameter recovery
  summary_calc <- function(results, method, fit, measure, func) {
    sapply(seq_along(results), function(i) {
      if (is.null(results[[i]][[method]][[fit]])) return(NA)
      else unlist(func(results[[i]][[method]][[fit]][[measure]], results[[i]][[measure]]))
    })
  }
  
  methods  <- c("bmlvar")
  measures <- c("beta", "pcor")
  funcs    <- list("rmse" = rmse_mean_list, "mse" = mse_mean_list, "bias" = bias_mean_list)
  
  for (method in methods) {
    for (measure in measures) {
      for (func_name in names(funcs)) {
        result_name <- paste(func_name, measure, method, sep = "_")
        calc_list   <- summary_calc(results, method, paste0("fit_", method),
                                    measure, funcs[[func_name]])
        mean_tmp <- colMeans(apply(as.matrix(calc_list), c(1, 2), as.numeric))
        ret[[paste0(result_name, "_mean")]] <- mean(mean_tmp)
        if (func_name == "rmse") {
          mse_tmp <- summary_calc(results, method, paste0("fit_", method),
                                  measure, funcs[["mse"]])
          mse_mean_tmp <- mean(colMeans(apply(as.matrix(mse_tmp), c(1, 2), as.numeric)))
          ret[[paste0(result_name, "_mcse")]] <- sqrt(stats::var(mean_tmp) /
                                                        (4 * n_rep * mse_mean_tmp))
        } else if (func_name == "mse") {
          ret[[paste0(result_name, "_mcse")]] <- sqrt(stats::var(mean_tmp) / n_rep)
        } else if (func_name == "bias") {
          ret[[paste0(result_name, "_mcse")]] <- sqrt(stats::var(mean_tmp) / n_rep)
        }
      }
    }
  }
  
  #--- Centrality rank-order
  calc_correlation <- function(results, method, measure) {
    sapply(seq_along(results), function(i) {
      if (is.null(results[[i]][[method]][[paste0("fit_", method)]])) return(NA)
      else stats::cor(results[[i]][[method]][[paste0("dens_", measure)]],
                      unlist(results[[i]]$true_cent[[paste0("dens_", measure)]]),
                      method = "spearman")
    })
  }
  
  bootstrap_rankcor <- function(data, n_boot) {
    bootstrap_res <- vector("numeric", n_boot)
    for (i in 1:n_boot) {
      ind <- sample(1:n_boot, replace = TRUE)
      bootstrap_res[i] <- mean(data[ind], na.rm = TRUE)
    }
    sd(bootstrap_res, na.rm = TRUE)
  }
  
  measures <- c("temp", "cont")
  for (method in methods) {
    for (measure in measures) {
      result_name <- paste("rankcor", measure, method, sep = "_")
      calc_list   <- calc_correlation(results = results, method = method, measure = measure)
      mean_tmp    <- mean(calc_list)
      sd_tmp      <- bootstrap_rankcor(calc_list, 1000)
      ret[[paste0(result_name, "_mean")]] <- mean_tmp
      ret[[paste0(result_name, "_mcse")]] <- sd_tmp
    }
  }
  
  #--- Most central node identification
  calc_most_cent_ident <- function(results, method, measure) {
    sapply(seq_along(results), function(i) {
      if (is.null(results[[i]][[method]][paste0("fit_", method)])) return(NA)
      else {
        mci <- most_cent_ident(results[[i]][[method]][[measure]],
                               results[[i]]$true_cent[[measure]])
        if (!is.vector(mci) | is.null(mci) | is.null(unlist(mci))) return(NA)
        colSums(matrix(unlist(mci), nrow = n_id, byrow = FALSE)) / n_id
      }
    })
  }
  
  measures <- c("instrength", "outstrength", "strength")
  for (method in methods) {
    for (measure in measures) {
      calc_list <- calc_most_cent_ident(results = results, method = method, measure = measure)
      mean_tmp  <- mean(calc_list, na.rm = TRUE)
      mcse_tmp  <- sqrt(mean_tmp * (1 - mean_tmp) / n_rep)
      if (measure == "outstrength") {
        ret[[paste0("mostcent_beta_", method, "_mean")]] <- mean_tmp
        ret[[paste0("mostcent_beta_", method, "_mcse")]] <- mcse_tmp
      } else if (measure == "strength") {
        ret[[paste0("mostcent_pcor_", method, "_mean")]] <- mean_tmp
        ret[[paste0("mostcent_pcor_", method, "_mcse")]] <- mcse_tmp
      }
    }
  }
  
  #--- Regression
  regression_power <- function(results, method, measure,
                               true_coef = 0.2, lm_beta = use_lm_beta) {
    sapply(seq_along(results), function(i) {
      if (is.null(results[[i]][[method]][[paste0("reg_", measure)]])) return(NA)
      else {
        reg_pvals <- sapply(results[[i]][[method]][[paste0("reg_", measure)]],
                            function(x) {
                              if (isTRUE(lm_beta)) {
                                res <- summary(lm.beta::lm.beta(x))$coefficients
                                res[2, 5]
                              } else {
                                res <- summary(x)$coefficients
                                res[2, 4]
                              }
                            })
        ifelse(reg_pvals < .05, 1, 0)
      }
    })
  }
  
  true_coef <- 0.2
  regression_summary <- function(results, method, measure,
                                  true_coef = 0.2, lm_beta = use_lm_beta,
                                  summary = "rmse") {
    sapply(seq_along(results), function(i) {
      if (is.null(results[[i]][[method]][[paste0("reg_", measure)]])) return(NA)
      else {
        reg_coefs <- sapply(results[[i]][[method]][[paste0("reg_", measure)]],
                            function(x) {
                              if (isTRUE(lm_beta)) lm.beta::lm.beta(x)$standardized.coefficients
                              else x$coefficients
                            })[2, ]
        if (summary == "rmse")       sqrt((reg_coefs - true_coef)^2)
        else if (summary == "mse")   (reg_coefs - true_coef)^2
        else if (summary == "bias")  reg_coefs - true_coef
      }
    })
  }
  
  methods   <- c("gvar", "mlvar", "gimme")
  measures  <- c("instrength", "outstrength", "strength")
  summaries <- c("rmse", "bias", "mse")
  
  # for (method in methods) {
  #   for (measure in measures) {
  #     for (summary in summaries) {
  #       result_name_summary <- paste(summary, "reg", measure, method, sep = "_")
  #       calc_list <- regression_summary(results = results, method = method,
  #                                       measure = measure, summary = summary)
  #       mean_tmp  <- mean(calc_list, na.rm = TRUE)
  #       names(mean_tmp) <- paste0(summary, "_reg2_", measure, "_", method, "_mean")
  #       ret[[paste0(result_name_summary, "_mean")]] <- mean_tmp
  #       if (summary == "rmse") {
  #         mse_tmp      <- regression_summary(results, method, measure, summary = "mse")
  #         mse_mean_tmp <- mean(mse_tmp, na.rm = TRUE)
  #         mcse_tmp     <- sqrt(var(calc_list, na.rm = TRUE) / (4 * n_rep * mse_mean_tmp))
  #         names(mcse_tmp) <- paste0(summary, "_reg2_", measure, "_", method, "_mcse")
  #         ret[[paste0(result_name_summary, "_mcse")]] <- mcse_tmp
  #       } else if (summary == "mse") {
  #         mcse_tmp <- sqrt(var(calc_list, na.rm = TRUE) / n_rep)
  #         names(mcse_tmp) <- paste0(summary, "_reg2_", measure, "_", method, "_mcse")
  #         ret[[paste0(result_name_summary, "_mcse")]] <- mcse_tmp
  #       } else if (summary == "bias") {
  #         mcse_bias <- sqrt(var(calc_list, na.rm = TRUE) / n_rep)
  #         names(mcse_bias) <- paste0(summary, "_reg2_", measure, "_", method, "_mcse")
  #         ret[[paste0(result_name_summary, "_mcse")]] <- mcse_bias
  #       }
  #       result_name_power <- paste("power", "reg", measure, method, sep = "_")
  #       calc_list_pwr <- regression_power(results = results, method = method, measure = measure)
  #       pwr_mean      <- mean(calc_list_pwr, na.rm = TRUE)
  #       names(pwr_mean) <- paste0("power_reg2_", measure, "_", method, "_mean")
  #       ret[[paste0(result_name_power, "_mean")]] <- pwr_mean
  #       pwr_mcse_tmp <- sqrt(pwr_mean * (1 - pwr_mean) / n_rep)
  #       names(pwr_mcse_tmp) <- paste0("power_reg2_", measure, "_", method, "_mcse")
  #       ret[[paste0(result_name_power, "_mcse")]] <- pwr_mcse_tmp
  #     }
  #   }
  # }
  
  # Summary for bmlvar
  method <- "bmlvar"
  regression_rmse_bmlvar <- function(results, method = "bmlvar",
                                     true_coef = 0.2, rmse = TRUE) {
    sapply(seq_along(results), function(i) {
      if (is.null(results[[i]][[method]][["reg_bmlvar"]])) return(NA)
      else {
        reg_coefs <- results[[i]][[method]][["reg_bmlvar"]][["regression_slope"]][["median"]]
        if (isTRUE(rmse)) sqrt((reg_coefs - true_coef)^2)
        else              (reg_coefs - true_coef)^2
      }
    })
  }
  
  regression_bias_bmlvar <- function(results, method = "bmlvar",
                                     true_coef = 0.2) {
    sapply(seq_along(results), function(i) {
      if (is.null(results[[i]][[method]][["reg_bmlvar"]])) return(NA)
      else {
        reg_coefs <- results[[i]][[method]][["reg_bmlvar"]][["regression_slope"]][["median"]]
        reg_coefs - true_coef
      }
    })
  }
  
  regression_power_bmlvar <- function(results, method = "bmlvar",
                                      measure, oneside = TRUE) {
    sapply(seq_along(results), function(i) {
      if (is.null(results[[i]][[method]][["reg_bmlvar"]])) return(NA)
      else {
        ci_twoside <- results[[i]][[method]][["reg_bmlvar"]][["regression_slope"]][["ci_95_l"]]
        ci_oneside <- results[[i]][[method]][["reg_bmlvar"]][["regression_slope"]][["ci_oneside"]]
        if (isTRUE(oneside)) ifelse(ci_oneside > 0, 1, 0)
        else                 ifelse(ci_twoside > 0, 1, 0)
      }
    })
  }
  
  calc_rmse        <- regression_rmse_bmlvar(results = results, method = "bmlvar", rmse = TRUE)
  calc_bias        <- regression_bias_bmlvar(results = results, method = "bmlvar")
  calc_mse         <- regression_rmse_bmlvar(results = results, method = "bmlvar", rmse = FALSE)
  calc_pwr_oneside <- regression_power_bmlvar(results = results, method = "bmlvar", oneside = TRUE)
  calc_pwr_twoside <- regression_power_bmlvar(results = results, method = "bmlvar", oneside = FALSE)
  
  measures <- c("instrength", "outstrength", "strength")
  
  mean_rmse <- rowMeans(calc_rmse, na.rm = TRUE)
  names(mean_rmse) <- paste0("rmse_reg2_", measures, "_bmlvar_mean")
  mean_bias <- rowMeans(calc_bias, na.rm = TRUE)
  names(mean_bias) <- paste0("bias_reg2_", measures, "_bmlvar_mean")
  mean_mse  <- rowMeans(calc_mse,  na.rm = TRUE)
  names(mean_mse)  <- paste0("mse_reg2_",  measures, "_bmlvar_mean")
  mean_pwroneside  <- rowMeans(calc_pwr_oneside, na.rm = TRUE)
  names(mean_pwroneside) <- paste0("poweroneside_reg2_", measures, "_bmlvar_mean")
  mean_pwrtwoside  <- rowMeans(calc_pwr_twoside, na.rm = TRUE)
  names(mean_pwrtwoside) <- paste0("powertwoside_reg2_", measures, "_bmlvar_mean")
  
  ret[["mean_rmse"]]       <- mean_rmse
  ret[["mean_bias"]]       <- mean_bias
  ret[["mean_mse"]]        <- mean_mse
  ret[["mean_pwroneside"]] <- mean_pwroneside
  ret[["mean_pwrtwoside"]] <- mean_pwrtwoside
  
  var_rmse  <- apply(calc_rmse, 1, stats::var)
  mcse_rmse <- sqrt(var_rmse / (4 * n_rep * mean_mse))
  names(mcse_rmse) <- paste0("rmse_reg2_", measures, "_bmlvar_mcse")
  
  var_bias  <- apply(calc_bias, 1, stats::var)
  mcse_bias <- sqrt(var_bias / n_rep)
  names(mcse_bias) <- paste0("bias_reg2_", measures, "_bmlvar_mcse")
  
  mcse_mse <- sqrt(mean_mse * (1 - mean_mse) / n_rep)
  names(mcse_mse) <- paste0("mse_reg2_", measures, "_bmlvar_mcse")
  
  mcse_pwroneside <- sqrt(mean_pwroneside * (1 - mean_pwroneside) / n_rep)
  names(mcse_pwroneside) <- paste0("poweroneside_reg2_", measures, "_bmlvar_mcse")
  
  mcse_pwrtwoside <- sqrt(mean_pwrtwoside * (1 - mean_pwrtwoside) / n_rep)
  names(mcse_pwrtwoside) <- paste0("powertwoside_reg2_", measures, "_bmlvar_mcse")
  
  ret[["mcse_rmse"]]       <- mcse_rmse
  ret[["mcse_bias"]]       <- mcse_bias
  ret[["mcse_mse"]]        <- mcse_mse
  ret[["mcse_pwroneside"]] <- mcse_pwroneside
  ret[["mcse_pwrtwoside"]] <- mcse_pwrtwoside
  
  #--- Return
  ret$bmlvar_diagnostics <- list()
  ret$bmlvar_diagnostics$rhat_bmlvar_mean   <- mean(sapply(results, function(x) x$bmlvar$rhat_bmlvar_mean))
  ret$bmlvar_diagnostics$rhat11_bmlvar_mean <- mean(sapply(results, function(x) x$bmlvar$rhat_bmlvar_11))
  ret$bmlvar_diagnostics$divtrans_bmlvar_mean   <- mean(sapply(results, function(x) x$bmlvar$divtrans_bmlvar))
  ret$bmlvar_diagnostics$divtrans_bmlvar_sum    <- sum(sapply(results,  function(x) x$bmlvar$divtrans_bmlvar))
  ret$bmlvar_diagnostics$divtrans_bmlvar_sumnonz <- sum(sapply(results, function(x) x$bmlvar$divtrans_bmlvar) > 0)
  
  ret_vec <- unlist(ret, use.names = TRUE)
  return(ret_vec)
}
```


# Executing Simulation

```{r run-sim}
n_rep     <- 30
n_workers <- 15
future::plan(multisession, workers = n_workers)

sim_results_rev2 <- SimDesign::runSimulation(
  design      = df_design[c(2,3),],
  replications = n_rep,
  generate     = sim_generate,
  analyse      = sim_analyse,
  summarise    = sim_summarise,
  fixed_objects = sim_pars,
  parallel     = "future",
  max_errors   = 2,
  control = list(include_replication_index = TRUE),
  packages     = c(
    "tidyverse",
    # "gimme",
    # "mlVAR",
    # "graphicalVAR",
    "lm.beta",
    "bayestestR",
    "posterior",
    "rstan",
    "corpcor",
    "Rcpp"
  ),
  save_results = TRUE,
  filename     = "sim_full_rev2_additional_only_bayes.rds"
)

plan(sequential)
```


# Write to standard R script

```{r, eval = FALSE}
knitr::purl(here::here("scripts", "09_additional_simulations_only_bayes.qmd"),
            output = here::here("scripts", "09_additional_simulations_only_bayes.R"),
            documentation = 2)
```


# Combine two iterations into one

We ran this script twice to avoid some computational issues with our server. These results were originally avilable as `sim_results_rev2_additional_only_bayes.rds` and `sim_results_rev2_additional_only_bayes_iter2.rds`. 
We here combine these results, averaging both point estimates and uncertainty.

```{r}
#| label: combine-results
#| eval: false

iter1 <- readRDS(here::here("output", "sim_results_rev2_additional_only_bayes.rds"))
iter2 <- readRDS(here::here("output", "sim_results_rev2_additional_only_bayes_iter2.rds"))


n1 <- 15
n2 <- 15
n_total <- n1 + n2

# initialize final dataframe
final_df <- iter1
final_df$REPLICATIONS <- n_total

# identify column categories
all_cols <- names(iter1)
mean_cols <- all_cols[grepl("_mean$", all_cols)]
mcse_cols <- all_cols[grepl("_mcse$", all_cols)]

# 1. combine diagnostic sums and counts
final_df$bmlvar_diagnostics.divtrans_bmlvar_sum <- iter1$bmlvar_diagnostics.divtrans_bmlvar_sum + 
                                                   iter2$bmlvar_diagnostics.divtrans_bmlvar_sum
final_df$bmlvar_diagnostics.divtrans_bmlvar_sumnonz <- iter1$bmlvar_diagnostics.divtrans_bmlvar_sumnonz + 
                                                       iter2$bmlvar_diagnostics.divtrans_bmlvar_sumnonz

# 2. process means and mcse values
for (m_col in mean_cols) {
  
  # calculate combined mean (arithmetic mean since n1 == n2)
  mu1 <- iter1[[m_col]]
  mu2 <- iter2[[m_col]]
  mu_comb <- (mu1 + mu2) / 2
  final_df[[m_col]] <- mu_comb
  
  # extract base name to find the corresponding mcse column
  base_name <- sub("mean_.*\\.", "", m_col) 
  base_name <- sub("_mean$", "", base_name)
  e_col <- mcse_cols[grepl(base_name, mcse_cols)][1]
  
  if (!is.na(e_col)) {
    se1 <- iter1[[e_col]]
    se2 <- iter2[[e_col]]
    
    # case a: binomial mcse (power and most central node identification)
    if (grepl("power|mostcent", m_col)) {
      final_df[[e_col]] <- sqrt(mu_comb * (1 - mu_comb) / n_total)
    } 
    
    # case b: rmse mcse (requires the specific mse mean for the denominator)
    else if (grepl("rmse", m_col)) {
      # locate the matching mse mean column for the rmse formula
      mse_col_name <- sub("rmse", "mse", base_name)
      mse_col <- mean_cols[grepl(mse_col_name, mean_cols)][1]
      
      mse_comb <- (iter1[[mse_col]] + iter2[[mse_col]]) / 2
      
      # reverse original mcse to recover the variance of the rmse components
      var1 <- se1^2 * (4 * n1 * iter1[[mse_col]])
      var2 <- se2^2 * (4 * n2 * iter2[[mse_col]])
      
      # pool the variances and calculate the new mcse
      var_pooled <- ((n1 - 1) * var1 + (n2 - 1) * var2) / (n_total - 1)
      final_df[[e_col]] <- sqrt(var_pooled / (4 * n_total * mse_comb))
    } 
    
    # case c: bias, mse, and rank correlation (standard variance pooling)
    else {
      # reverse out the sample variance from the mcse
      var1 <- se1^2 * n1
      var2 <- se2^2 * n2
      
      # use pooled variance formula (includes the difference between means)
      var_pooled <- ((n1 - 1) * var1 + (n2 - 1) * var2 + (n1 * n2 / n_total) * (mu1 - mu2)^2) / (n_total - 1)
      final_df[[e_col]] <- sqrt(var_pooled / n_total)
    }
  }
}


saveRDS(final_df, here::here("output", "rev2", "sim_full_rev2_additional_only_bayes.rds"))

```


We additionally conduct some unit testing/sanity checks to see if the aggregation worked as intended: 

```{r}
#| label: sanity-check-aggregation

# loop-based sanity check
for (col in names(final_df)) {
  v1 <- iter1[[col]]; v2 <- iter2[[col]]; vc <- final_df[[col]]
  
  # skip non-numeric or static condition columns
  if (is.character(vc) || col %in% names(final_df)[1:7]) next
  
  if (grepl("_mean$", col)) {
    # check if combined mean is the exact midpoint
    if (!all(abs(vc - (v1 + v2) / 2) < 1e-10)) stop(paste("mean failed:", col))
    
  } else if (grepl("_mcse$", col)) {
    # check if pooled mcse is smaller than the maximum individual mcse
    # note: we use a small tolerance for cases where pooled variance increases slightly
    if (!all(vc <= pmax(v1, v2) + 1e-10)) stop(paste("mcse failed:", col))
    
  } else if (grepl("_sum|_sumnonz", col)) {
    # check if sums are exactly additive
    if (!all(vc == (v1 + v2))) stop(paste("sum failed:", col))
  }
}

# check replication count
if (any(final_df$REPLICATIONS != 30)) stop("replication count incorrect")


```

